---
title: "Appendix A: PIBKC Bycatch in the Groundfish Fisheries"
author: "William T. Stockhausen"
institute: NOAA/NMFS/AFSC
date: '`r format(Sys.time(), "%b %e, %Y")`'
fontsize: 11pt 
number-sections: false
reference-location: document
reference-section-title: References
bibliography: '`r path.expand("~/Work/Projects/Bibliography/AllRefs.bib")`'
csl: '`r system.file("files/CJFAS.csl",package="wtsQMD")`'
link-citations: true
crossref:
  chapters: false      # prepend label reference numbers by chater number?
  fig-title: Figure    # for caption: default is "Figure")
  tbl-title: Table     # for caption: default is "Table")
  title-delim: "."     # for caption: default is ":")
  fig-prefix: Figure   # for in-text (use [-@fig-ref] to drop prefix in text)
  tbl-prefix: Table    # for in-text (use [-@tbl-ref] to drop prefix in text)
  fig-labels: arabic    # options are arabic, roman, roman i, alpha x, alpha X; latter two starting from x/X
  tbl-labels: arabic    # options are arabic, roman, roman i, alpha x, alpha X; latter two starting from x/X
  subref-labels: alpha a # options are arabic, roman, roman i, alpha x, alpha X; latter two starting from x/X
  ref-hyperlink: true    # references are hyperlinked if true
format: 
  html: 
    df-print: paged
    toc: true
    toc-location: right
    fig-width: 8
    fig-asp: 1.4
    fig-dpi: 100
    embed-resources: true
  pdf:
    documentclass: scrartcl
    toc: false
    fig_crop: false
    keep-tex: false
    geometry:
      - left=1.0in
      - right=1.0in
      - top=1.0in
      - bottom=1.0in
      - textwidth=6.5in
      - showframe=false
    include-in-header: 
      - text: |
          \usepackage{placeins}
          \extrafloats{500}
          \maxdeadcycles=10000
      - file: "/Users/williamstockhausen/Work/Programming/R/Library/wtsQMD/files/ltx_ExtraLatexIncludes.tex"
echo: false
warning: false
results: 'hide'
keep-md: false
keep-tex: false
keep-yaml: false
editor: source
editor_options: 
  chunk_output_type: console
concordance: true
params:
  setup: !expr 'system.file("files/qmd_setup.R",package="wtsQMD")'
  testing: false
---
<!-- IMPORTANT: if used as a child doc, all chunk labels must be unique within the overall document -->

<!-- 
  NOTEs: 
     * child_path$peek() gives path to current script.
     * before starting a child document, do 
         "child_path$push(file.path(child_path$peek(),rel_path))" first, 
         where rel_path is the relative path to the child
     * after a child document has finished, do "child_path$pop()" to return to current path value
-->

## Bycatch in the groundfish fisheries {#sec-GroundfishFisheries}

<!-- if not child doc, set up required objects -->
```{r}
#| label: GFD_setup
#| eval: !expr '!knitr::opts_knit$get("child")'
#| results: "asis"
  if (!exists("testing")) testing = params$testing;
  if (testing) cat(params$setup,"\n\n")
  source(params$setup);
  if (testing) {
    cat("In GFD_setup:\n\n")
    cat("root = ",root,"\n\n");
    cat("peek = '",child_path$peek(),"'\n\n",sep="");
  }
```

```{r}
#| label: setup_GFD
#| results: 'asis'
  require(ggplot2);
  require(kableExtra);
  require(tables);
  Sum = wtsUtilities::Sum;
  old_thm = ggplot2::theme_set(cowplot::theme_cowplot(font_size = 10) +
                               cowplot::background_grid() +
                               cowplot::panel_border());
  thm = wtsPlots::getStdTheme();
  options("readr.show_col_types"=FALSE);
  if (testing) cat("dirThs =",child_path$peek(),"\n\n")
  if (!exists("prj_setup")){
    fn = file.path(child_path$peek(),"../../rda_AssessmentSetup.RData");
    if (child_path$peek()=="") fn = file.path(rstudioapi::getActiveProject(),
                                              "rda_AssessmentSetup.RData");
    prj_setup = wtsUtilities::getObj(fn);
  }
  gfr = wtsUtilities::getObj(prj_setup$fnData_GFs);
  last5Fxd = gfr$dfrLast5AvgByGearType |> dplyr::filter(gear=="fixed");
  last5Trl = gfr$dfrLast5AvgByGearType |> dplyr::filter(gear=="trawl");
```

Bycatch estimates of PIBKC in the groundfish fisheries are based on groundfish observer data sampling expanded to total catch. Historical estimates beginning in 1991/92 are available to 2008/09 from AKFIN using results from the old Catch Accounting System database. This data is limited in its spatial resolution to NMFS statistical areas, which do not conform to the PIBKC stock area. As with previous assessments, estimates of blue king crab bycatch in the groundfish fisheries from NMFS statistical area 513 are assumed to account for bycatch within the PIBKC stock area.  More recent estimates, 2009/10-present, are available from AKFIN using results from the AKRO's Catch-In-Areas database, which provides standardized spatial resolution using ADF&G statistical areas (among other improvements over the older Catch Accounting System). In 2019, the algorithm used by AKFIN to expand observer data was changed from one based on retained groundfish catch weight to the one currently used by AKRO, which is based on total groundfish catch weight. This was applied retroactively to data from calendar year 2017 forward, affecting estimates for crab starting in crab year 2016.

Here, bycatch in the groundfish fisheries during `r gfr$timeFrame` is documented. The data were downloaded from AKFIN on `r gfr$downloadDate` for the current assessment. In order to apply gear-specific discard mortality rates to the bycatch data, trawl gear types (pelagic and non-pelagic) have been aggregated as "trawl" gear, while hook-and-line (longline) and pot gear have been aggregated as "fixed" gear. As in previous assessments, discard mortality rates of `r gfr$hm.fxd` and `r gfr$hm.trl` have subsequently been applied by gear type (fixed and trawl, respectively) to the estimated bycatch biomass to estimate fishing-related mortality for the discarded crab [@PIBKC2021; @PIBKC2023]. Since 2009/10, the maximum annual bycatch of PIBKC in the groundfish fisheries was `r numKGinT(gfr$maxByc)` in `r crabYear(gfr$maxBycYr)`, while the maximum total discard mortality was `r numKGinT(gfr$maxMrt)` in `r crabYear(gfr$maxMrtYr)`. In contrast, the average bycatch over the last 5 years is `r numKGinT(gfr$avgByc5)`, while the average discard mortality is `r numKGinT(gfr$avgMrt5)`.

### Bycatch by gear type

Annual estimates of bycatch abundance, biomass, and discard mortality of PIBKC in the groundfish fisheries are presented in Table [-@tbl-GFBbyGearType] and Figures [-@fig-GFBbyGearType1] and [-@fig-GFBbyGearType2] by (aggregated) gear type. In general, trawl gear takes more PIBKC than fixed gear, and with higher mortality, although exceptions occur (e.g., 2011/12, 2013/14, 2014/15, and 2023/24). The average mortality on PIBKC taken by trawl gear over the last five years is `r numKGinT(last5Trl$mortality)` while that taken by fixed gear is `r numKGinT(last5Fxd$mortality)`.

```{r tblGFBbyGearType}
#| results: asis
tmp = gfr$dfrBycatchByGearType |> 
        dplyr::mutate(year=crabYear(year),
                      number=round(number),
                      biomass=round(biomass),
                      mortality=round(mortality),
                      gear=paste(gear,"gear"));

tblr<-tables::tabular(Heading(Year)*Factor(year)~
                       Heading(`Gear Type`)*Factor(gear)*
                        (Heading(number)*number+
                         Heading(biomass)*biomass+
                         Heading(mortality)*mortality)*sum,
                      data=tmp);
colLabels(tblr)<-colLabels(tblr)[2:3,]; #remove unnecessary headings
kbl = wtsQMD::convert_tblr_to_kbl(tblr,c(1,4),isHTM,replaceNAs="--") |> 
        kableExtra::column_spec(c(1,4),border_right=TRUE);
cap<-paste0("Bycatch of PIBKC in the BSAI groundfish fisheries, by gear type. ",
            "Biomass and (discard) mortality are in kilograms. ",
            "Bycatch in numbers is only available after 2008/09. ",
            "Discard mortality rates of ",gfr$hm.fxd," and ",gfr$hm.trl,
            " for fixed and trawl gear, respectively, ",
            "were applied to the biomass estimates to obtain discard mortalities for all years.");
  lstTbls = c(lstTbls,
              insertKblIntoQMD(kbl,
                               lbl="tbl-GFBbyGearType", 
                               cap=cap,
                               ori="P"));
rm(lbl,cap,kbl,tmp,tblr);
```

### Bycatch by target type

Annual estimates of bycatch abundance, biomass, and discard mortality of PIBKC in the groundfish fisheries are presented by groundfish target type in Tables [-@tbl-GFBAbdByTargetType]-[-@tbl-GFBMrtByTargetType] and Figure [-@fig-GFBbyTargetType]. Groundfish targets with less than 10 kg bycatch over the `r wtsQMD::crabYear(2009)`-`r gfr$strYr` period have been dropped. PIBKC is primarily taken as bycatch in fisheries targeting flathead sole, yellowfin sole, northern rock sole, and Pacific cod. Although the Pacific cod fishery accounted for the highest bycatch of PIBKC by weight (in 2015) across the time series, it generally ranks below the other fisheries as a source of mortality because the bycatch occurs primarily with fixed gear. In 2023/24, however, it was the target fishery that accounted for the largest source of PIBKC mortality ([@tbl-GFBMrtByTargetType], [@fig-GFBbyTargetType]).

```{r tblGFBAbdByTargetType}
#| results: asis
tmp = gfr$dfrBycatchByTargetType |> 
        dplyr::mutate(year=crabYear(year),
                      number=round(number),
                      target=stringr::str_remove(target,stringr::fixed(" - BSAI")));
#----bycatch abundance
tblr<-tables::tabular(Heading(Year)*Factor(year)~
                       Heading(`Target Type`)*Factor(target)*(Heading(number)*number)*sum,
                      data=tmp);
colLabels(tblr)<-colLabels(tblr)[2:3,]; #remove the "sum" headings
kbl = wtsQMD::convert_tblr_to_kbl(tblr,c(1),isHTM);
# lbl = wtsQMD::getLabel();
cap<-paste0("Estimated bycatch (numbers of crab, rounded to whole numbers) of PIBKC in the groundfish fisheries, by target type ",
            "(avalable only after 2008/09). ",
            "Discard mortality rates have not been applied.");
# lstTbls[[lbl]] = list(lbl=lbl,cap=cap,tbl=kbl);
  lstTbls = c(lstTbls,
              insertKblIntoQMD(kbl,
                               lbl="tbl-GFBAbdByTargetType", 
                               cap=cap,
                               ori="P"));
rm(lbl,cap,kbl,tmp,tblr);
```

```{r tblGFBBioByTargetType}
#| results: asis
tmp = gfr$dfrBycatchByTargetType |> 
        dplyr::mutate(year=crabYear(year),
                      biomass=round(biomass),
                      target=stringr::str_remove(target,stringr::fixed(" - BSAI")));
#----bycatch biomass
tblr<-tables::tabular(Heading(Year)*Factor(year)~
                       Heading(`Target Type`)*Factor(target)*(Heading(biomass)*biomass)*sum,
                      data=tmp);
colLabels(tblr)<-colLabels(tblr)[2:3,]; #remove the "sum" headings
kbl = wtsQMD::convert_tblr_to_kbl(tblr,c(1),isHTM);
#lbl = wtsQMD::getLabel();
cap<-paste0("Estimated bycatch (biomass, in kg) of PIBKC in the groundfish fisheries, by target type ",
            "(avalable only after 2008/09). ",
            "Discard mortality rates have not been applied.");
# lstTbls[[lbl]] = list(lbl=lbl,cap=cap,tbl=kbl);
  lstTbls = c(lstTbls,
              insertKblIntoQMD(kbl,
                               lbl="tbl-GFBBioByTargetType", 
                               cap=cap,
                               ori="P"));
rm(lbl,cap,kbl,tmp,tblr);
```

```{r tblGFBMrtByTargetType}
#| results: asis
tmp = gfr$dfrBycatchByTargetType |> 
        dplyr::mutate(year=crabYear(year),
                      mortality=round(mortality),
                      target=stringr::str_remove(target,stringr::fixed(" - BSAI")));
#----bycatch biomass
tblr<-tables::tabular(Heading(Year)*Factor(year)~
                       Heading(`Target Type`)*Factor(target)*(Heading(mortality)*mortality)*sum,
                      data=tmp);
colLabels(tblr)<-colLabels(tblr)[2:3,]; #remove the "sum" headings
kbl = wtsQMD::convert_tblr_to_kbl(tblr,c(1),isHTM);
#lbl = wtsQMD::getLabel();
cap<-paste0("Estimated discard mortality (in kg) of PIBKC in the BSAI groundfish fisheries, by target type.",
            "Discard mortality rates of ",gfr$hm.fxd," and ",gfr$hm.trl," for ",
            "fixed and trawl gear, respectively, were applied to bycatch estimates to obtain discard mortalities for all years.");
# lstTbls[[lbl]] = list(lbl=lbl,cap=cap,tbl=kbl);
  lstTbls = c(lstTbls,
              insertKblIntoQMD(kbl,
                               lbl="tbl-GFBMrtByTargetType", 
                               cap=cap,
                               ori="P"));
rm(lbl,cap,kbl,tmp,tblr);
```

### Spatial patterns of bycatch

Spatial patterns of PIBKC bycatch, by ADF&G stat area, in the groundfish fisheries are illustrated by gear type in Figures [-@fig-GFB-TrawlGearMap] and [-@fig-GFB-FixedGearMap]. Bycatch taken with trawl gear tends to be concentrated along and to the northeast of the eastern boundary of the Habitat Conservation Zone (non-pelagic trawl gear is excluded from the Zone), although 2012 was an exception in which bycatch was concentrated along the western edge of the Zone. In contrast, bycatch taken by fixed gear is typically dispersed along the shelf edge, although it was concentrated within and near the Pribilof Islands Habitat Conservation Zone (area outlined in red in Figures [-@fig-GFB-TrawlGearMap] and [-@fig-GFB-FixedGearMap]) in 2015/16 and again in 2023/24.

```{r}
#| label: fig-GFBbyGearType1
  #--plot bycatch and discard mortality by gear type
  tmp = gfr$dfrBycatchByGearType;#--biomass in kg
  p1 <- ggplot(tmp,aes(x=year,y=biomass/1000,colour=gear)) + 
          geom_line(size=1.0) + labs(x="crab year",y="Biomass (t)") + ylim(0,NA) + 
          scale_x_continuous(breaks = seq(1900,2100,5)) + 
          guides(colour=guide_legend(nrow=1,title="gear type:")) + 
          theme(legend.position=c(0.99,0.99),
                legend.justification=c(1,1),
                legend.direction="horizontal");
  p2 <- ggplot(tmp,aes(x=year,y=mortality/1000,colour=gear)) + 
          geom_line(size=1.0) + 
          labs(x="crab year",y="Discard Mortality (t)") + 
          ylim(0,NA) + 
          scale_x_continuous(breaks = seq(1900,2100,5)) + 
          guides(colour=guide_legend(nrow=1,title="gear type:")) + 
          theme(legend.position="none",legend.direction="horizontal");
  pg = cowplot::plot_grid(p1,p2,ncol=1)
  lbl = wtsQMD::getLabel();
  cap<-paste0("Upper plot: Bycatch of PIBKC in the groundfish fisheries since 1991/92 by gear type (no mortality applied). ",
              "Lower plot: Discard mortality of PIBKC in the groundfish fisheries since 1991/92 by gear type. ",
              "Gear-specific discard mortality rates of ",gfr$hm.fxd," and ",gfr$hm.trl,
              " were applied to bycatch from fixed and trawl gear, respectively.");
  pth = wtsQMD::getFigFN();
  lstFigs[[lbl]] = list(lbl=lbl,cap=cap,pth=pth,wid=def_wid,dpi=def_dpi);
  ggsave(pth,plot=pg,width=def_wid,height=6,units="in",dpi=def_dpi);
  rm(tmp,p1,p2,pg,lbl,cap,pth);
```

```{r}
#| label: fig-GFBbyGearType2
  #--plot bycatch and discard mortality by gear type
  tmp = gfr$dfrBycatchByGearType |> dplyr::filter(year>=2009);#--biomass in kg
  p1 <- ggplot(tmp,aes(x=year,y=biomass/1000,colour=gear)) + 
          geom_line(size=1.0) + labs(x="crab year",y="Biomass (t)") + ylim(0,NA) + 
          scale_x_continuous(breaks = seq(1900,2100,1)) + 
          guides(colour=guide_legend(nrow=1,title="gear type:")) + 
          theme(legend.position=c(0.99,0.99),
                legend.justification=c(1,1),
                legend.direction="horizontal");
  p2 <- ggplot(tmp,aes(x=year,y=mortality/1000,colour=gear)) + 
          geom_line(size=1.0) + 
          labs(x="crab year",y="Discard Mortality (t)") + 
          ylim(0,NA) + 
          scale_x_continuous(breaks = seq(1900,2100,1)) + 
          guides(colour=guide_legend(nrow=1,title="gear type:")) + 
          theme(legend.position="none",legend.direction="horizontal");
  pg = cowplot::plot_grid(p1,p2,ncol=1)
  lbl = wtsQMD::getLabel();
  cap<-paste0("Upper plot: Bycatch of PIBKC in the groundfish fisheries since 2009/10 by gear type (no mortality applied). ",
              "Lower plot: Discard mortality of PIBKC in the groundfish fisheries since 2009/10 by gear type. ",
              "Gear-specific discard mortality rates of ",gfr$hm.fxd," and ",gfr$hm.trl,
              " were applied to bycatch from fixed and trawl gear, respectively.");
  pth = wtsQMD::getFigFN();
  lstFigs[[lbl]] = list(lbl=lbl,cap=cap,pth=pth,wid=def_wid,dpi=def_dpi);
  ggsave(pth,plot=pg,width=def_wid,height=6,units="in",dpi=def_dpi);
  rm(tmp,p1,p2,pg,lbl,cap,pth);
```

```{r}
#| label: fig-GFBbyTargetType
  #--plot bycatch and discard mortality by target type
  tmp = gfr$dfrBycatchByTargetType |> 
          dplyr::mutate(target=stringr::str_remove(target,stringr::fixed(" - BSAI")));

  p1 <- ggplot(tmp,aes(x=year,y=biomass/1000,colour=target)) + 
          geom_line(size=1.0) + labs(x="crab year",y="Biomass (t)") + ylim(0,NA) + 
          scale_x_continuous(breaks = min(tmp$year):max(tmp$year)) + 
          guides(colour=guide_legend(nrow=1,title="target:")) + 
          theme(legend.position=c(0.99,0.99),
                legend.justification=c(1,1),
                legend.direction="horizontal");
  p2 <- ggplot(tmp,aes_string(x="year",y="mortality",colour="target")) + 
          geom_line(size=1.0) + 
          labs(x="crab year",y="Discard Mortality (kg)") + 
          ylim(0,NA) + 
          scale_x_continuous(breaks = min(tmp$year):max(tmp$year)) + 
          guides(colour=guide_legend(nrow=1,title="gear type:")) + 
          theme(legend.position="none",legend.direction="horizontal");
  pg = cowplot::plot_grid(p1,p2,ncol=1)
  lbl = wtsQMD::getLabel();
  cap<-paste0("Upper plot: Bycatch of PIBKC in the groundfish fisheries since 2009/10 by target type (no mortality applied). ",
              "Lower plot: Discard mortality of PIBKC in the groundfish fisheries since 2009/10 by target type. ",
              "Gear-specific discard mortality rates of ",gfr$hm.fxd," and ",gfr$hm.trl,
              " were applied to bycatch from fixed and trawl gear, respectively.");
  pth = wtsQMD::getFigFN();
  lstFigs[[lbl]] = list(lbl=lbl,cap=cap,pth=pth,wid=def_wid,dpi=def_dpi);
  ggsave(pth,plot=pg,width=def_wid,height=6,units="in",dpi=def_dpi);
  rm(tmp,p1,p2,pg,lbl,cap,pth);
```

```{r}
#| label: GFD-CalcMaps
  #----create EBS basemap
  crsWGS84<-wtsGIS::get_crs("WGS84");
  bbox = wtsGIS::getBBox(list(bottomleft=list(lon=-175,lat=55),
                              topright  =list(lon=-166,lat=59)))
  basemap = wtsGIS::gg_CreateBasemapLayers(bbox=bbox);
  #----create statistical areas and PI Habitat Conservation Area layers
  stat.polys<-wtsGIS::readShapefile(file.path(gfr$gisDir,
                                              "ADFG Statistical Areas/ADFG_StatAreas_EBS.shp"),
                                    crs=crsWGS84) |>  
                wtsGIS::cropFeaturesToBBox(bbox);
  hca<-wtsGIS::readShapefile(file.path(gfr$gisDir,
                                       "ConservationAreas/pribilof_hca.shp"),
                             crs=crsWGS84);#--no need to crop features
  #------calc catch by gear type and stat area
  tbl = gfr$dfrBycatchDetails |> 
          dplyr::group_by(year,gear,`stat area`) |> 
          dplyr::summarize(biomass=sum(biomass),
                           number=sum(number)) |> 
          dplyr::ungroup() |> 
          dplyr::mutate(`stat area`=as.character(`stat area`));
  sfCatch = wtsGIS::mergeDataframeWithLayer(tbl,stat.polys,
                                            dataID="stat area",geomsID="STAT_AREA",
                                            sfJoinType="left join",
                                            spAllData=FALSE,spDuplicateGeoms=TRUE);
  mxB = max(sfCatch$biomass);
  rm(crsWGS84,bbox,stat.polys,tbl);
```

```{r}
#| label: fig-GFB-TrawlGearMap
  tmp = sfCatch |> dplyr::filter(gear=="trawl",biomass>0)
  p = ggplot() + basemap + 
        geom_sf(aes(fill=biomass),data=tmp) + 
        geom_sf(data=hca,inherit.aes=FALSE,colour="red",fill=NA,linewidth=1) + 
        scale_fill_viridis_c(option="magma",direction=-1,limits=c(0,mxB),alpha=0.9) + 
        facet_wrap(~year) + 
        theme(axis.text=element_blank())
  lbl = wtsQMD::getLabel();
  cap<-paste0("Estimated bycatch of PIBKC in the groundfish trawl gear fisheries ",
              "by ADF&G stat area, expanded from groundfish observer reports. ",
              "Red line: boundary of the PIHCZ.");
  pth = wtsQMD::getFigFN();
  lstFigs[[lbl]] = list(lbl=lbl,cap=cap,pth=pth,wid=def_wid,dpi=def_dpi);
  ggsave(pth,plot=p,width=def_wid,height=6.5,units="in",dpi=def_dpi);
  rm(tmp,p,lbl,cap,pth);
```

```{r}
#| label: fig-GFB-FixedGearMap
  tmp = sfCatch |> dplyr::filter(gear=="fixed",biomass>0)
  p = ggplot() + basemap + 
        geom_sf(aes(fill=biomass),data=tmp) + 
        geom_sf(data=hca,inherit.aes=FALSE,colour="red",fill=NA,linewidth=1) + 
        scale_fill_viridis_c(option="magma",direction=-1,limits=c(0,mxB),alpha=0.9) + 
        facet_wrap(~year) + 
        theme(axis.text=element_blank())
  lbl = wtsQMD::getLabel();
  cap<-paste0("Estimated bycatch of PIBKC in the groundfish fixed gear fisheries ",
              "by ADF&G stat area, expanded from groundfish observer reports. ",
              "Red line: boundary of the PIHCZ.");
  pth = wtsQMD::getFigFN();
  lstFigs[[lbl]] = list(lbl=lbl,cap=cap,pth=pth,wid=def_wid,dpi=def_dpi);
  ggsave(pth,plot=p,width=def_wid,height=6.5,units="in",dpi=def_dpi);
  rm(tmp,p,lbl,cap,pth);
```

```{r}
#| label: GFD_cleanup
  rm(basemap,hca);#--add gfr?
```

<!-- references -->
```{r refs_GFD,eval=!knitr::opts_knit$get("child"),results='asis'}
  cat("# References {-}\n");
  cat("::: {#refs}\n");
  cat(":::\n\n");
```

<!-- tables, if not child doc and lstTbls is not empty -->
```{r}
#| label: tables_GFD
#| eval: !expr '!knitr::opts_knit$get("child")'
#| results: asis
  source(system.file("files/printTablesSectionFromList.R",package="wtsQMD"));
```

<!-- figures, if not child doc and lstFigs is not empty -->
```{r}
#| label: figures_GFD
#| eval: !expr '!knitr::opts_knit$get("child")'
#| results: asis
  source(system.file("files/printFiguresSectionFromList.R",package="wtsQMD"));
```

