---
title: "Comparison of NMFS survey results with and without corner stations"
author: "William T. Stockhausen"
institute: NOAA/NMFS/AFSC
date: '`r format(Sys.time(), "%b %e, %Y")`'
fontsize: 11pt 
number-sections: true
reference-location: document
bibliography: '`r path.expand("~/Work/Projects/Bibliography/AllRefs.bib")`'
csl: '`r system.file("files/CJFAS.csl",package="wtsQMD")`'
link-citations: true
crossref:
  chapters: false      # prepend label reference numbers by chater number?
  fig-title: Figure    # for caption: default is "Figure")
  tbl-title: Table     # for caption: default is "Table")
  title-delim: "."     # for caption: default is ":")
  fig-prefix: Figure   # for in-text (use [-@fig-ref] to drop prefix in text)
  tbl-prefix: Table    # for in-text (use [-@tbl-ref] to drop prefix in text)
  fig-labels: arabic    # options are arabic, roman, roman i, alpha x, alpha X; latter two starting from x/X
  tbl-labels: arabic    # options are arabic, roman, roman i, alpha x, alpha X; latter two starting from x/X
  subref-labels: alpha a # options are arabic, roman, roman i, alpha x, alpha X; latter two starting from x/X
  ref-hyperlink: true    # references are hyperlinked if true
format: 
  html: 
    df-print: paged
    toc: true
    toc-location: right
    fig-width: 8
    fig-asp: 1.4
    fig-dpi: 100
    embed-resources: true
    include-in-header: 
      - '`r system.file("files/in-line_math_mode.html",package="wtsQMD")`'
  pdf:
    documentclass: scrartcl
    toc: false
    fig_crop: false
    keep-tex: false
    geometry:
      - left=1.0in
      - right=1.0in
      - top=1.0in
      - bottom=1.0in
      - textwidth=6.5in
      - showframe=false
    include-in-header: 
      - text: |
          \usepackage{placeins}
          \extrafloats{500}
          \maxdeadcycles=10000
      - file: '`r system.file("files/ltx_ExtraLatexIncludes.tex",package="wtsQMD")`'
echo: false
warning: false
results: 'hide'
keep-md: false
keep-yaml: false
editor: source
editor_options: 
  chunk_output_type: console
concordance: true
params:
  setup: !expr 'system.file("files/qmd_setup.R",package="wtsQMD")'
  dirAsmt: "~/Work/StockAssessments-Crab/Assessments/TannerCrab/2024-09_TannerCrab/AssessmentData/Data_Surveys_NMFS"
  testing: false
---
<!-- IMPORTANT: if used as a child doc, all chunk labels must be unique within the overall document -->

<!-- 
  NOTEs: 
     * child_path$peek() gives path to current script folder.
     * before starting a child document, do 
         "child_path$push(file.path(child_path$peek(),rel_path))" first, 
         where rel_path is the relative path to the child
     * after a child document has finished, do "child_path$pop()" to return to current path value
-->

<!-- if not child doc, set up required objects -->
```{r}
#| label: NCS_setup
#| eval: !expr '!knitr::opts_knit$get("child")'
#| results: "asis"
  testing = params$testing;
  if (testing) cat(params$setup,"\n\n")
  source(params$setup);
  if (testing) cat("root = ",root,"\n\n")
```

```{r}
#| label: setup_NCS
#| results: 'asis'
  require(crabpack);
  require(ggplot2);
  require(kableExtra);
  require(tables);
  
  #--path to folder containing "this" file
  dirThs = child_path$peek();

  #--constants
  MILLION  = 1000000;
  THOUSAND = 1000;

  #--survey years to include
  yrs = 1975:2024;
```

```{r NCS-getSurveyData}
  #--get my PIBKC crab survey results (run r_wts.PIBKC.doCalcs.R)----
  lstWCS = wtsUtilities::getObj(file.path(dirThs,"../02_CrabpackDataComparisons/rda_wts.PIBKC.NMFS.RData"));
  
  #--PIBKC data calculated without corner stations----
  lstNCS = wtsUtilities::getObj(file.path(dirThs,"rda_wts.PIBKC.NMFS.NoCornerStations.RData"));
```

```{r NCS-calcSurveyABs}
  #--Biomass and abundance----
  ##--extract biomass/abundance time series for PIBKC with corner stations
  dfrWCS_ABs = lstWCS$dfrACD.ByX.PD |> 
                  dplyr::select(y=YEAR,
                                STRATUM_AREA,
                                xm=SEX,
                                x=SEXp,
                                abd=totABUNDANCE,
                                abdCV=cvABUNDANCE,
                                bio=totBIOMASS,
                                bioCV=cvBIOMASS) |> 
                  dplyr::mutate(type="WCS",
                                abd=MILLION*abd,
                                bio=THOUSAND*bio);
  #head(dfrWCS_ABs);
  ##--extract biomass/abundance time series for PIBKC with corner stations
  dfrNCS_ABs = lstNCS$dfrACD.ByX.PD |> 
                  dplyr::select(y=YEAR,
                                STRATUM_AREA,
                                xm=SEX,
                                x=SEXp,
                                abd=totABUNDANCE,
                                abdCV=cvABUNDANCE,
                                bio=totBIOMASS,
                                bioCV=cvBIOMASS) |> 
                  dplyr::mutate(type="NCS",
                                abd=MILLION*abd,
                                bio=THOUSAND*bio);
  #head(dfrWCS_ABs);
  
  dfrABs = dplyr::bind_rows(dfrWCS_ABs,dfrNCS_ABs);

  #--calculate differences in biomass
  dfrBsp = dfrABs |> dplyr::select(y,xm,bio,type) |> 
              tidyr::pivot_wider(names_from="type",values_from="bio") |> 
              dplyr::mutate(diff=WCS-NCS,
                            pdif=2*100*diff/(WCS+NCS));
```

## No corner stations {#sec-NCS}

As part of the effort to "modernize" the NMFS EBS bottom trawl survey to improve efficiency, the high-density "corner" stations in the NMFS EBS survey grid near the Pribilof Islands and St. Matthew Island ([@fig-NCS-SurveyBasemap]) were dropped for the 2024 survey and will not be sampled in future surveys. Assessment authors were asked to consider the impact of this change on their assessment. This section compares the estimates of mature male biomass (MMB) and other population components derived from previous surveys with corner stations with those obtained by dropping the corner stations in order to obtain a retrospective idea of the importance of the corner stations to estimates of the PIBKC MMB time series.

```{r}
#| label: fig_NCS-SurveyBasemap
#| results: asis
#| fig-width: 6.5 
#| fig-asp: 1.0
  gisPath = "~/Work/StockAssessments-Crab/Data/GIS/Shapefiles";
  #----create EBS basemap
  crsWGS84<-wtsGIS::get_crs("WGS84");
  bbox = wtsGIS::getBBox(list(bottomleft=list(lon=-175,lat=55),
                              topright  =list(lon=-166,lat=59)))
  basemap = wtsGIS::gg_CreateBasemapLayers(bbox=bbox);
  #--get survey grid layers
  grid = (tcsamSurveyData::gisGetSurveyGridLayers()$grid) |> 
           wtsGIS::cropFeaturesToBBox(bbox);

  # #----create PI Habitat Conservation Area layers
  # hca = wtsGIS::readShapefile(file.path(gisPath,
  #                                       "ConservationAreas/pribilof_hca.shp"),
  #                             crs=crsWGS84);#--no need to crop features
  #--EBS survey grid
  p = ggplot() + basemap +
        geom_sf(data=grid,fill=NA) + 
        geom_sf(data=lstWCS$evs.stns |> dplyr::filter(YEAR==2023),colour="blue",alpha=0.9);# + 
        # geom_sf(data=hca,fill=NA,colour="orange",linewidth=1);
  lbl = wtsQMD::getLabel();
  cap = paste0("The NMFS EBS Shelf Survey survey grid cells (thin black lines) and nominal sampling stations (large dots) ",
               'in the Pribilof District. The "corner" stations in the grid circles (16 stations) were dropped in 2024 and ',
               'will not be revisited during the survey for the foreseeable future.');
  pth = wtsQMD::getFigFN();
  lstFigs = c(lstFigs,wtsQMD::printGGplot(p,lbl=lbl,cap=cap,pth=pth,ori="P"));
  rm(p,lbl,cap,pth);
```

### Survey biomass estimates

Estimates of biomass from the NMFS EBS bottom trawl survey for different components of the PIBKC stock are compared by year in [@fig-NCS-SrvBio] for calculations made including or excluding the corner stations. Absolute differences and percent differences between the sets of survey stations are shown, respectively, in Figures [-@fig-NCS-SrvBioAbsDif] and [-@fig-NCS-SrvBioPctDif]. The percent differences are also shown in Table [-@tbl-NCS-SrvBioPctDif]. Figures [-@fig-NCS-MMB] and [-@fig-NCS-MMBlog ] provide more detailed looks at the differences between the two sets of survey stations. 

Estimates of PIBKC MMB were generally higher when the corner stations were included: 25 years versus 17 years when excluding the corner stations resulted in a higher estimate. Since 2013, including the corner stations resulted in higher (or equal) estimates in all years except 2023 and 2024 when no mature males were caught anywhere.



```{r}
#| label: fig_NCS-SrvBio
#| results: asis
#| fig-width: 9
#| fig-asp: 0.7
  p1 = ggplot(dfrABs |> dplyr::mutate(bio=bio/THOUSAND) |> dplyr::filter(y<1985),
              aes(x=y,y=bio,ymin=bio*(1-bioCV),ymax=bio*(1+bioCV),colour=type,fill=type,shape=type)) + 
       geom_ribbon(alpha=0.3,colour=NA) + geom_line() + geom_point(fill=NA,size=3) + 
       scale_fill_manual(values=c("gold","blue"),aesthetics=c("colour","fill")) + 
       scale_x_continuous(breaks=seq(1970,3000,2)) +
       scale_shape_manual(values=c(24,25)) + 
       facet_grid(xm~.,scales="free") + 
       labs(y="Biomass (1000's t)") + 
       wtsPlots::getStdTheme() + 
       theme(axis.title.x=element_blank(),
             legend.title=element_blank(),
             strip.text.y=element_blank(),
             legend.position="none",
             legend.position.inside=c(0.99,0.99),
             legend.justification=c(1,1));
  p2 = ggplot(dfrABs |> dplyr::mutate(bio=bio/THOUSAND) |> dplyr::filter(y>=1985),
              aes(x=y,y=bio,ymin=bio*(1-bioCV),ymax=bio*(1+bioCV),colour=type,fill=type,shape=type)) + 
       geom_ribbon(alpha=0.3,colour=NA) + geom_line() + geom_point(fill=NA,size=3) + 
       scale_fill_manual(values=c("gold","blue"),aesthetics=c("colour","fill")) + 
       scale_x_continuous(breaks=seq(1970,3000,5)) +
       scale_shape_manual(values=c(24,25)) + 
       facet_grid(xm~.,scales="free") + 
       labs(y="Biomass (1000's t)") + 
       wtsPlots::getStdTheme() + 
       theme(axis.title.x=element_blank(),
             axis.title.y=element_blank(),
             legend.title=element_blank(),
             legend.position="inside",
             legend.position.inside=c(0.99,0.99),
             legend.justification=c(1,1));
  pg = cowplot::plot_grid(p1,p2,nrow=1,rel_widths=c(1,2.5));
  cap = paste0("Comparison of annual estimates of design-based area-swept biomass ",
               "from the NMFS EBS bottom trawl survey by the 2023 PIBKC assessment (*asmt*) and ",
               "the `crabpack` R package (*crabpack*), by population category.");
  lbl = wtsQMD::getLabel();
  pth = wtsQMD::getFigFN();
  lstFigs = c(lstFigs,wtsQMD::printGGplot(pg,lbl=lbl,cap=cap,pth=pth,ori="L"));
```

```{r}
#| label: fig_NCS-SrvBioAbsDif
#| results: asis
#| fig-width: 9
#| fig-asp: 0.7
  p1 = ggplot(dfrBsp |> dplyr::mutate(diff=diff/THOUSAND) |> dplyr::filter(y<1985),
              aes(x=y,y=diff)) + 
       geom_line() + geom_point(fill=NA,size=3) + 
       geom_hline(yintercept=0,linetype=3) + 
       scale_fill_manual(values=c("gold","blue"),aesthetics=c("colour","fill")) + 
       scale_x_continuous(breaks=seq(1970,3000,2)) +
       scale_shape_manual(values=c(24,25)) + 
       facet_grid(xm~.) + 
       labs(y="Biomass Difference (1,000's t)") + 
       wtsPlots::getStdTheme() + 
       theme(axis.title.x=element_blank(),
             strip.text.y=element_blank(),
             legend.title=element_blank(),
             legend.position="none",
             legend.position.inside=c(0.99,0.99),
             legend.justification=c(1,1));
  p2 = ggplot(dfrBsp |> dplyr::mutate(diff=diff/THOUSAND) |> dplyr::filter(y>=1985),
              aes(x=y,y=diff)) + 
       geom_line() + geom_point(fill=NA,size=3) + 
       geom_hline(yintercept=0,linetype=3) + 
       scale_fill_manual(values=c("gold","blue"),aesthetics=c("colour","fill")) + 
       scale_x_continuous(breaks=seq(1970,3000,5)) +
       scale_shape_manual(values=c(24,25)) + 
       facet_grid(xm~.) + 
       labs(y="Biomass Difference (1,000's t)") + 
       wtsPlots::getStdTheme() + 
       theme(axis.title.x=element_blank(),
             axis.title.y=element_blank(),
             legend.title=element_blank(),
             legend.position="inside",
             legend.position.inside=c(0.99,0.99),
             legend.justification=c(1,1));
  pg = cowplot::plot_grid(p1,p2,nrow=1,rel_widths=c(1,2.5));
  cap = paste0("Differences in annual estimates of design-based area-swept biomass ",
               "from the NMFS EBS bottom trawl survey by the 2023 PIBKC assessment and ",
               "the `crabpack` R package, by population category.");
  lbl = wtsQMD::getLabel();
  pth = wtsQMD::getFigFN();
  lstFigs = c(lstFigs,wtsQMD::printGGplot(pg,lbl=lbl,cap=cap,pth=pth,ori="L"));
```

```{r}
#| label: fig_NCS-SrvBioPctDif
#| results: asis
#| fig-width: 9
#| fig-asp: 0.7
  p1 = ggplot(dfrBsp |> dplyr::filter(y<1985), aes(x=y,y=pdif)) + 
       geom_line() + geom_point(fill=NA,size=3) + 
       geom_hline(yintercept=0,linetype=3) + 
       scale_fill_manual(values=c("gold","blue"),aesthetics=c("colour","fill")) + 
       scale_x_continuous(breaks=seq(1970,3000,2)) +
       scale_shape_manual(values=c(24,25)) + 
       facet_grid(xm~.) + 
       labs(y="% Difference in Biomass") + 
       wtsPlots::getStdTheme() + 
       theme(axis.title.x=element_blank(),
             strip.text.y=element_blank(),
             legend.title=element_blank(),
             legend.position="none",
             legend.position.inside=c(0.99,0.99),
             legend.justification=c(1,1));
  p2 = ggplot(dfrBsp |> dplyr::filter(y>=1985), aes(x=y,y=pdif)) + 
       geom_line() + geom_point(fill=NA,size=3) + 
       geom_hline(yintercept=0,linetype=3) + 
       scale_fill_manual(values=c("gold","blue"),aesthetics=c("colour","fill")) + 
         scale_x_continuous(breaks=seq(1970,3000,5)) +
       scale_shape_manual(values=c(24,25)) + 
       facet_grid(xm~.) + 
       labs(y="% Difference in Biomass") + 
       wtsPlots::getStdTheme() + 
       theme(axis.title.x=element_blank(),
             axis.title.y=element_blank(),
             legend.title=element_blank(),
             legend.position="inside",
             legend.position.inside=c(0.99,0.99),
             legend.justification=c(1,1));
  pg = cowplot::plot_grid(p1,p2,nrow=1,rel_widths=c(1,2.5));
  cap = paste0("Percent differences in annual estimates of design-based area-swept biomass ",
               "from the NMFS EBS bottom trawl survey by the 2023 PIBKC assessment and ",
               "the `crabpack` R package, by population category.");
  lbl = wtsQMD::getLabel();
  pth = wtsQMD::getFigFN();
  lstFigs = c(lstFigs,wtsQMD::printGGplot(pg,lbl=lbl,cap=cap,pth=pth,ori="L"));
```

```{r tbl.NCS-SrvBioPctDif}
#| results: asis
  tblr = tabular(Factor(y,name="year") ~ Factor(xm)*pdif*mean,
                 data=dfrBsp |> dplyr::mutate(pdif=round(pdif,1)));
  colLabels(tblr) = colLabels(tblr)[2,];
  kbl = tblr |> wtsQMD::convert_tblr_to_kbl(col_spec=c(1),isHTM,
                                            ltx_font_size=7,replaceNAs="--",adjColSpacing=-4);
  cap = paste0("Percent difference, by year, in design-based NMFS survey biomass trends ",
               "from the 2023 PIBKC assessment and the `crabpack` R package, by population category. ",
               "NaN: indicates that no crab in the category were caught.");
  lstTbls = c(lstTbls,
              wtsQMD::insertKblIntoQMD(kbl,
                                       lbl="tbl-NCS-SrvBioPctDif", 
                                       cap=cap,
                                       ori="P"));
  rm(tblr,kbl,cap);
```

```{r}
#| label: fig-NCS-MMB
#| results: asis
#| fig-width: 9
#| fig-asp: 0.7
  tmp = dfrABs |> dplyr::filter(xm=="mature males");
  p1 = ggplot(tmp |> dplyr::mutate(bio=bio/THOUSAND),
              aes(x=y,y=bio,ymin=bio*(1-bioCV),ymax=bio*(1+bioCV),colour=type,fill=type,shape=type)) + 
       geom_ribbon(alpha=0.3,colour=NA) + geom_line() + geom_point(fill=NA,size=3) + 
       geom_hline(yintercept=0,linetype=3) + 
       scale_fill_manual(values=c("gold","blue"),aesthetics=c("colour","fill")) + 
       scale_x_continuous(breaks=seq(1970,3000,5)) +
       scale_shape_manual(values=c(24,25)) + 
       facet_grid(xm~.,scales="free") + 
       labs(y="Biomass (1000's t)") + 
       wtsPlots::getStdTheme() + 
       theme(axis.title.x=element_blank(),
             legend.title=element_blank(),
             strip.text.y=element_blank(),
             legend.position="inside",
             legend.position.inside=c(0.99,0.99),
             legend.justification=c(1,1));
  p2 = ggplot(tmp |> dplyr::mutate(bio=bio/THOUSAND) |> dplyr::filter(y>2010),
              aes(x=y,y=bio,ymin=bio*(1-bioCV),ymax=bio*(1+bioCV),colour=type,fill=type,shape=type)) + 
       geom_ribbon(alpha=0.3,colour=NA) + geom_line() + geom_point(fill=NA,size=3) + 
       geom_hline(yintercept=0,linetype=3) + 
       scale_fill_manual(values=c("gold","blue"),aesthetics=c("colour","fill")) + 
       scale_x_continuous(breaks=seq(1970,3000,2)) +
       scale_shape_manual(values=c(24,25)) + 
       facet_grid(xm~.,scales="free") + 
       labs(y="Biomass (1000's t)") + 
       wtsPlots::getStdTheme() + 
       theme(axis.title.x=element_blank(),
             legend.title=element_blank(),
             strip.text.y=element_blank(),
             legend.position="inside",
             legend.position.inside=c(0.99,0.99),
             legend.justification=c(1,1));
  pg = cowplot::plot_grid(p1,p2,ncol=1);
  cap = paste0('Comparison of time series of PIBKC MMB obtained by including corner stations ("WCS") ',
               'and excluding them ("NCS"). Note that corner stations were not sampled in 1975-1981 and 2024. ',
               "Additionally, no survey was conducted in 2020.");
  lbl = wtsQMD::getLabel();
  pth = wtsQMD::getFigFN();
  lstFigs = c(lstFigs,wtsQMD::printGGplot(pg,lbl=lbl,cap=cap,pth=pth,ori="L"));
```

```{r}
#| label: fig-NCS-MMBlog
#| results: asis
#| fig-width: 9
#| fig-asp: 0.7
  tmp = dfrABs |> dplyr::filter(xm=="mature males");
  p1 = ggplot(tmp |> dplyr::mutate(bio=bio/THOUSAND),
              aes(x=y,y=bio,ymin=bio*(1-bioCV),ymax=bio*(1+bioCV),colour=type,fill=type,shape=type)) + 
       geom_ribbon(alpha=0.3,colour=NA) + geom_line() + geom_point(fill=NA,size=3) + 
       geom_hline(yintercept=0,linetype=3) + 
       scale_fill_manual(values=c("gold","blue"),aesthetics=c("colour","fill")) + 
       scale_x_continuous(breaks=seq(1970,3000,5)) + 
       scale_y_log10(limits=c(0.03,NA)) + 
       scale_shape_manual(values=c(24,25)) + 
       facet_grid(xm~.,scales="free") + 
       labs(y="Biomass (1000's t)") + 
       wtsPlots::getStdTheme() + 
       theme(axis.title.x=element_blank(),
             legend.title=element_blank(),
             strip.text.y=element_blank(),
             legend.position="inside",
             legend.position.inside=c(0.99,0.99),
             legend.justification=c(1,1));
  p2 = ggplot(tmp |> dplyr::mutate(bio=bio/THOUSAND) |> dplyr::filter(y>2010),
              aes(x=y,y=bio,ymin=bio*(1-bioCV),ymax=bio*(1+bioCV),colour=type,fill=type,shape=type)) + 
       geom_ribbon(alpha=0.3,colour=NA) + geom_line() + geom_point(fill=NA,size=3) + 
       geom_hline(yintercept=0,linetype=3) + 
       scale_fill_manual(values=c("gold","blue"),aesthetics=c("colour","fill")) + 
       scale_x_continuous(breaks=seq(1970,3000,2)) +
       scale_y_log10() + 
       scale_shape_manual(values=c(24,25)) + 
       facet_grid(xm~.,scales="free") + 
       labs(y="Biomass (1000's t)") + 
       wtsPlots::getStdTheme() + 
       theme(axis.title.x=element_blank(),
             legend.title=element_blank(),
             strip.text.y=element_blank(),
             legend.position="inside",
             legend.position.inside=c(0.99,0.99),
             legend.justification=c(1,1));
  pg = cowplot::plot_grid(p1,p2,ncol=1);
  cap = paste0('Comparison of time series of PIBKC MMB obtained by including corner stations ("WCS") ',
               'and excluding them ("NCS"). Note that corner stations were not sampled in 1975-1981 and 2024. ',
               "Additionally, no survey was conducted in 2020.");
  lbl = wtsQMD::getLabel();
  pth = wtsQMD::getFigFN();
  lstFigs = c(lstFigs,wtsQMD::printGGplot(pg,lbl=lbl,cap=cap,pth=pth,ori="L"));
```

<!-- references, if not child doc -->
```{r,eval=!knitr::opts_knit$get("child"),results='asis'}
  cat("# References {-}\n");
  cat("::: {#refs}\n");
  cat(":::\n\n");
```

<!-- tables, if not child doc and lstTbls is not empty -->
```{r}
#| label: tables_NCS
#| eval: !expr '!knitr::opts_knit$get("child")'
#| results: asis
  source(system.file("files/printTablesSectionFromList.R",package="wtsQMD"));
```

<!-- figures, if not child doc and lstFigs is not empty -->
```{r}
#| label: figures_NCS
#| eval: !expr '!knitr::opts_knit$get("child")'
#| results: asis
  source(system.file("files/printFiguresSectionFromList.R",package="wtsQMD"));
```
