---
title: "sdmTMB estimation of PIBKC mature male biomass from the NMFS EBS survey"
author: "William T. Stockhausen"
institute: NOAA/NMFS/AFSC
date: '`r format(Sys.time(), "%b %e, %Y")`'
fontsize: 11pt 
number-sections: true
reference-location: document
bibliography: '`r path.expand("~/Work/Projects/Bibliography/AllRefs.bib")`'
csl: '`r system.file("files/CJFAS.csl",package="wtsQMD")`'
link-citations: true
crossref:
  chapters: false      # prepend label reference numbers by chater number?
  fig-title: Figure    # for caption: default is "Figure")
  tbl-title: Table     # for caption: default is "Table")
  title-delim: "."     # for caption: default is ":")
  fig-prefix: Figure   # for in-text (use [-@fig-ref] to drop prefix in text)
  tbl-prefix: Table    # for in-text (use [-@tbl-ref] to drop prefix in text)
  fig-labels: arabic    # options are arabic, roman, roman i, alpha x, alpha X; latter two starting from x/X
  tbl-labels: arabic    # options are arabic, roman, roman i, alpha x, alpha X; latter two starting from x/X
  subref-labels: alpha a # options are arabic, roman, roman i, alpha x, alpha X; latter two starting from x/X
  ref-hyperlink: true    # references are hyperlinked if true
format: 
  html: 
    df-print: paged
    toc: true
    toc-location: right
    fig-width: 8
    fig-asp: 1.4
    fig-dpi: 100
    embed-resources: true
    include-in-header: 
      - '`r system.file("files/in-line_math_mode.html",package="wtsQMD")`'
  pdf:
    documentclass: scrartcl
    toc: false
    fig_crop: false
    keep-tex: true
    geometry:
      - left=1.0in
      - right=1.0in
      - top=1.0in
      - bottom=1.0in
      - textwidth=6.5in
      - showframe=false
    include-in-header: 
      - text: |
          \usepackage{placeins}
          \extrafloats{500}
          \maxdeadcycles=10000
      - file: '`r system.file("files/ltx_ExtraLatexIncludes.tex",package="wtsQMD")`'
echo: false
warning: false
results: 'hide'
keep-md: true
keep-yaml: false
editor: source
editor_options: 
  chunk_output_type: console
concordance: true
params:
  setup: !expr 'system.file("files/qmd_setup.R",package="wtsQMD")'
  dirAsmt: "~/Work/StockAssessments-Crab/Assessments/TannerCrab/2024-09_TannerCrab/AssessmentData/Data_Surveys_NMFS"
  testing: false
---
<!-- IMPORTANT: if used as a child doc, all chunk labels must be unique within the overall document -->

<!-- 
  NOTEs: 
     * child_path$peek() gives path to current script folder.
     * before starting a child document, do 
         "child_path$push(file.path(child_path$peek(),rel_path))" first, 
         where rel_path is the relative path to the child
     * after a child document has finished, do "child_path$pop()" to return to current path value
-->

<!-- if not child doc, set up required objects -->
```{r}
#| label: PIBKC_sdmTMB_setup
#| eval: !expr '!knitr::opts_knit$get("child")'
#| results: "asis"
  testing = params$testing;
  if (testing) cat(params$setup,"\n\n")
  source(params$setup);
  if (testing) cat("root = ",root,"\n\n")
```

```{r}
#| label: setup_PIBKC_sdmTMB
#| results: 'asis'
  require(crabpack);
  require(ggplot2);
  require(kableExtra);
  require(tables);
  
  #--path to folder containing "this" file
  dirThs = child_path$peek();
  if (rstudioapi::isAvailable()) dirThs = dirname(rstudioapi::getActiveDocumentContext()$path);

  #--constants
  MILLION  = 1000000;
  THOUSAND = 1000;

  #--survey years to include
  yrs = 1975:2024;
```

## Introduction

As noted in the previous section, the NMFS EBS bottom trawl survey captured no mature male PIBKC in 2023 and 2024, introducing problematic zeros into the survey MMB time series that the `rema` model is used to smooth. It was suggested that making assumptions regarding the sampling distribution for mature males was a simple way to develop "reasonable" replacement values for the zeros when using `rema` to obtain the smoothed time series. Although probably better than filling in the zeros with an arbitrary "small" number (as suggested in the `rema` documentation) or simply dropping the zeros from the time series, the suggested method does not avoid requiring possibly arbitrary assumptions regarding the underlying sampling distribution and/or appropriate detection level. One significant drawback to this approach is that it makes the implicit assumption that all sampling locations are statistically interchangeable and independent. In fact, PIBKC mature males have undergone a range contraction over time, as well as a decline in overall abundance/biomass (e.g., [@fig-sdmTMB-MapsMMB]), indicating that the sampling locations are not interchangeable or independent.

Another, more satisfying, alternative for "filling in the zeros" would be to use a spatiotemporal model such as provided by the VAST [@VAST2015] or sdmTMB [@sdmTMB2024] R packages. Either package provides the ability to statistically model and estimate trends and variability in stock biomass through space and time given spatially-explicit data such as the NMFS EBS bottom trawl survey provides. Here, I investigated the use of sdmTMB, a more user-friendly alternative to VAST, to estimate a stock biomass time series for PIBKC mature males in the context of survey sampling results that captured no crab in multiple years.

```{r}
#| label: fig_sdmTMB-MapsMMB
#| results: asis
#| fig-width: 9 
#| fig-asp: 1.0

  lbl = wtsQMD::getLabel();
  cap = paste0("CPUE (1,000's t/sq. nmi.) for mature male PIBKC biomass from the NMFS EBS bottom trawl survey for selected years, ",
               "illustrating the range contraction and decline in population size over time. ",
               "The survey has sampled PIBKC annually since 1975 (with the exception of 2020). No mature males were caught in 2023 or 2024.")
  pth = wtsQMD::getImageFN(file.path(dirThs,"fig_Map-CPUE"));
  lstFigs = c(lstFigs,wtsQMD::printGGplot(NULL,lbl=lbl,cap=cap,pth=pth,ori="L"));
  rm(lbl,cap,pth);
```

### sdmTMB 

sdmTMB is an R package that fits spatiotemporal Generalized Linear Mixed Effects Models (GLMMs) using Template Model Builder (TMB), R-INLA, and Gaussian Markov random fields. One common application is to create species distribution models (SDMs) from species abundance data collected across space and through time, although its principal advantage here is that it can also estimate stock-level time series by integrating estimated spatially-explicit patterns of abundance or biomass across space. A simple way to think about an sdmTMB model is that it provides a way to interpolate survey observations across space and time, taking into account both population variability across space and time as well as variability inherent to the sampling process itself.

Here, four sdmTMB models ([@tbl-sdmTMB-Models]) were fit to spatially-explicit annual survey CPUE data (biomass/unit area) for PIBKC mature males using a spatial mesh defined by the sampling locations in UTM coordinates and a cutoff of 5 km ([-@fig-sdmTMB-Mesh]). Two of the four models, "m3" and "m3-ar" were two-stage "delta-gamma" models that used a binomial family with a log-link to model presence/absence of mature males in a survey haul (the delta model) and a gamma family with a log-link to model non-zero CPUE given that mature males were caught in the given survey haul (the gamma model). Both models included the survey haul depth as a possible covariate, with the possible effects on presence/absence or non-zero CPUE estimated as a smoothly-varying function of ln(depth). Spatiotemporal residuals were modeled as a random walk process in m3; in m3-ar, they were modeled as a first-order autoregressive process. Additionally, the spatial correlation was allowed to be anisotropic and Restricted Maximum Likelihood (REML) was used to fit both models. The remaining two models, "tw" and "tw-ar", were similar to their respective `m3` counterparts except that models used the Tweedie distribution [@Tweedie1984] with a log-link as the statistical basis for the fit rather than a delta-gamma model.

```{r tbl_sdmTMB-Models}
#| results: "asis"
  #--sdmTMB model descriptions
  dfrDscr = tibble::tribble(~model,~type,~`link(s)`,~residuals,~covariates,~`anisotropic?`,~`REML?`,
      "m3","delta-gamma","log","random walk","log(bottom depth)","true","true",
      "m3-ar","delta-gamma","log","AR(1)","log(bottom depth)","true","true",
      "tw","Tweedie","log","random walk","log(bottom depth)","true","true",
      "tw-ar","Tweedie","log","AR(1)","log(bottom depth)","true","true"
                            );
  kbl = kableExtra::kbl(dfrDscr) |> 
          kableExtra::kable_styling(bootstrap_options="striped",
                                    latex_options="striped");
  cap = paste0("Brief descriptions of the four sdmTMB models.")
  lstTbls = c(lstTbls,
              wtsQMD::insertKblIntoQMD(kbl,
                                       lbl=paste0("tbl-sdmTMB-Models"),
                                       cap=cap,
                                       ori="P"));
  rm(kbl,cap);
```

```{r}
#| label: fig_sdmTMB-Mesh
#| results: asis
#| fig-width: 6.5 
#| fig-asp: 1.0

  #--get the MMB survey data
  dfrCPUE_MM = wtsUtilities::getObj(file.path(dirThs,"rda_CPUE_MM.RData"));

  #--mesh3<-sdmTMB::make_mesh(dfrCPUE_MM,c("X","Y"),cutoff=5,type="cutoff");
  mesh3 = wtsUtilities::getObj(file.path(dirThs,"rda_meshes.RData"))$mesh3;
  
  p = ggplot() + inlabru::gg(mesh3$mesh) +
        labs(subtitle="cutoff=5") +
        geom_point(data=dfrCPUE_MM,mapping=aes(x=X,y=Y)) + 
        labs(x="UTM (km)",y="UTM (km)") + 
        wtsPlots::getStdTheme();
  lbl = wtsQMD::getLabel();
  cap = paste0("The spatial mesh generated by sdmTMB and used for the sdmTMB models. ",
               "The points indicate the NMFS EBS bottom trawl survey sampling locations usd to create the mesh.");
  pth = wtsQMD::getFigFN();
  lstFigs = c(lstFigs,wtsQMD::printGGplot(p,lbl=lbl,cap=cap,pth=pth,ori="P"));
  rm(p,lbl,cap,pth);
```

```{r sdmTMB_GetModelResults}
  fn = file.path(dirThs,"rda_mdls-all_log_depth-st_rw-dg.RData");
  if (file.exists(fn)) {
    lstMdls = wtsUtilities::getObj(fn);
  } else {
    lst1 = wtsUtilities::getObj(file.path(dirThs,"rda_mdls_log_depth-st_rw-dg.RData"));
    lst2 = wtsUtilities::getObj(file.path(dirThs,"rda_mdls_ar_log_depth-st_rw-dg.RData"));
    lstMdls = c(lst1,lst2);
    rm(lst1,lst2);
  }
  names(lstMdls) = stringr::str_replace(stringr::str_remove(names(lstMdls),"mdl_"),"_","-");
  lstMdls = lstMdls[sort(names(lstMdls))];
```

```{r tbl_sdmTMB_ModelResults}
#| results: "asis"
  ##--print results----
  for (mdl in names(lstMdls)){
    #--mdl = names(lstMdls)[2];
    str = paste0("###--Results for model ",mdl,"----");
    strp = capture.output(print(lstMdls[[mdl]]));
    dfr = tibble::tibble(title=strp);
    names(dfr) = str;
    kbl = kableExtra::kbl(dfr,booktabs=TRUE,linesep="")  |> 
          kableExtra::kable_styling(bootstrap_options="basic",
                                    latex_options="basic");
    cap = paste0("Summary of results for model '",mdl,"'.")
    lstTbls = c(lstTbls,
                wtsQMD::insertKblIntoQMD(kbl,
                                         lbl=paste0("tbl-sdmTMB-ModelResults-",mdl),
                                         cap=cap,
                                         ori="P"));
  }
  rm(mdl,str,strp,dfr,kbl,cap);
```

```{r tbl_sdmTMB-AICs}
#| results: "asis"
  #--compare AICs----
  lst = list();
  for (mdl_ in names(lstMdls)){
    lst[[mdl_]] = tibble::tibble(model=mdl_,AIC=AIC(lstMdls[[mdl_]]));
  }
  dfrAICs = dplyr::bind_rows(lst);
  kbl = kableExtra::kbl(dfrAICs) |> 
          kableExtra::kable_styling(bootstrap_options="striped",
                                    latex_options="striped");
  cap = paste0("AIC scores for the four sdmTMB models.")
  lstTbls = c(lstTbls,
              wtsQMD::insertKblIntoQMD(kbl,
                                       lbl=paste0("tbl-sdmTMB-AICs"),
                                       cap=cap,
                                       ori="P"));
  rm(lst,mdl,dfrAICs,kbl,cap);
```

```{r}
#| label: fig_sdmTMB-Indices
#| results: asis
#| fig-width: 6.5
#| fig-asp: 1.0
  #--get indices----
  dfrACD_MM  = wtsUtilities::getObj(file.path(dirThs,"rda_ACD_MM.RData"));  
  lstIdxs = wtsUtilities::getObj(file.path(dirThs,"rda_idxs_log_depth-st_rw-dg.RData"));
  names(lstIdxs) = stringr::str_replace(stringr::str_remove(names(lstIdxs),"mdl_"),"_","-");

  ##--extract and plot sdmTMB indices----
  lstIdxs1 = list();
  for (mdl in names(lstMdls)){
    lstIdxs1[[mdl]] = lstIdxs[[mdl]] |>
                        dplyr::select(year,pred=est,pred_lci=lwr,pred_uci=upr,se) |>
                        dplyr::mutate(option=mdl,
                                      pred_cv=se/pred) |>
                        dplyr::select(!se);
  }
  dfrIdxs = dplyr::bind_rows(lstIdxs1);
  p1 = ggplot(dfrIdxs,aes(x=year,y=pred,ymin=pred_lci,ymax=pred_uci,colour=option,fill=option)) +
        geom_ribbon(alpha=0.3) + geom_point() + geom_line() +
        geom_point(data=dfrACD_MM,mapping=aes(x=YEAR,y=3.4299*totBIOMASS),colour="blue",inherit.aes=FALSE) +
        labs(y="biomass (1,000's t)") +
        wtsPlots::getStdTheme();
  p2 = ggplot(dfrIdxs,aes(x=year,y=pred,ymin=pred_lci,ymax=pred_uci,colour=option,fill=option)) +
        geom_ribbon(colour=NA,alpha=0.5) + geom_line() +
        geom_vline(xintercept=2020) +
        geom_vline(xintercept=2023:2024,linetype=3) +
        geom_point(data=dfrACD_MM,mapping=aes(x=YEAR,y=3.4299*totBIOMASS),colour="blue",inherit.aes=FALSE) +
        scale_y_log10() +
        labs(y="biomass (1,000's t)") +
        wtsPlots::getStdTheme();
  
  pg = cowplot::plot_grid(p1,p2,ncol=1);
  lbl = wtsQMD::getLabel();
  cap = paste0("Biomass time series for mature male PIBKC, as estimated by each of the four sdmTMB models. ",
               "Blue dots indicate the estimates obtained using design-based calculations.");
  pth = wtsQMD::getFigFN();
  lstFigs = c(lstFigs,wtsQMD::printGGplot(pg,lbl=lbl,cap=cap,pth=pth,ori="P"));
```

```{r}
#| label: fig_sdmTMB-REMA
#| results: asis
#| fig-width: 6.5
#| fig-asp: 1.0
  #--get REMA results and combine with sdmTMB results----
  lstREMAs = wtsUtilities::getObj(file.path(dirThs,"../04_SamplingBasedZerosSubstitutions/rda_Zeros_REMA_Models.RData"));
  options = c(unique(lstREMAs$dfrPrds$option)[3:5],unique(dfrIdxs$option));
  dfrIdxs1 = lstREMAs$dfrPrds |>
              dplyr::filter(option %in% options) |>
              dplyr::mutate(obs=3.4299*obs/1000,
                           obs_lci=3.4299*obs_lci/1000,
                           obs_uci=3.4299*obs_uci/1000,
                           pred=3.4299*pred/1000,
                           pred_lci=3.4299*pred_lci/1000,
                           pred_uci=3.4299*pred_uci/1000
                           ) |>
              dplyr::bind_rows(dfrIdxs) |>
              dplyr::mutate(option=factor(option,levels=c(options,"sdmTMB")));
  #--make plots----
  p1 = ggplot(dfrIdxs1,aes(x=year,y=pred,ymin=pred_lci,ymax=pred_uci,colour=option,fill=option)) +
    geom_ribbon(alpha=0.3,colour=NA) + geom_point() + geom_line() +
    geom_point(data=dfrACD_MM,mapping=aes(x=YEAR,y=3.4299*totBIOMASS),colour="blue",inherit.aes=FALSE) +
    labs(y="predicted biomass (1,000's t)") +
    wtsPlots::getStdTheme();
  p2 = ggplot(dfrIdxs1,aes(x=year,y=pred,ymin=pred_lci,ymax=pred_uci,colour=option,fill=option)) +
    geom_vline(xintercept=2020) +
    geom_vline(xintercept=2023:2024,linetype=3) +
    geom_ribbon(alpha=0.3,colour=NA) + geom_point() + geom_line() +
    geom_point(data=dfrACD_MM,mapping=aes(x=YEAR,y=3.4299*totBIOMASS),colour="blue",inherit.aes=FALSE) +
    scale_y_log10() +
    labs(y="predicted biomass (1,000's t)") +
    wtsPlots::getStdTheme();
  p3 = ggplot(dfrIdxs1 |> dplyr::filter(year>2000),
         aes(x=year,y=pred,ymin=pred_lci,ymax=pred_uci,colour=option,fill=option)) +
    geom_vline(xintercept=2020) +
    geom_vline(xintercept=2023:2024,linetype=3) +
    geom_ribbon(alpha=0.3,colour=NA) + geom_point() + geom_line() +
    geom_point(data=dfrACD_MM |> dplyr::filter(YEAR>2000),
               mapping=aes(x=YEAR,y=3.4299*totBIOMASS),colour="blue",inherit.aes=FALSE) +
    scale_y_log10() +
    labs(y="predicted biomass (1,000's t)") +
    wtsPlots::getStdTheme();
  pg = cowplot::plot_grid(p1,p2,p3,ncol=1);

  lbl = wtsQMD::getLabel();
  cap = paste0("Biomass time series for mature male PIBKC, as estimated using each of the `rema` zeros options ",
               "and the four sdmTMB models. ",
               "Blue dots indicate the estimates obtained using design-based calculations.");
  pth = wtsQMD::getFigFN();
  lstFigs = c(lstFigs,wtsQMD::printGGplot(pg,lbl=lbl,cap=cap,pth=pth,ori="P"));
rm(p1,p2,p3,pg,lbl,cap,pth);
```

```{r}
#| label: fig_sdmTMB-Residuals
#| results: asis
#| fig-width: 9
#| fig-asp: 1.0

  lstRes = wtsUtilities::getObj(file.path(dirThs,"rda_resids_log_depth-st_rw-dg.RData"));
  names(lstRes) = stringr::str_replace(stringr::str_remove(names(lstRes),"mdl_"),"_","-");
  lstRes = lstRes[sort(names(lstRes))];
  for (mdl in names(lstMdls)){
    lbl = wtsQMD::getLabel(xtra=mdl);
    cap = paste0("DHAMRa residuals diagnostics plots for '",mdl,"'.");
    pth = wtsQMD::getFigFN(xtra=mdl);
    lstFigs = c(lstFigs,wtsQMD::printRGraphics(expression(plot(lstRes[[mdl]])),lbl=lbl,cap=cap,pth=pth,ori="L"));
  }
rm(lstRes,mdl,lbl,cap,pth);
```


<!-- references, if not child doc -->
```{r,eval=!knitr::opts_knit$get("child"),results='asis'}
  cat("# References {-}\n");
  cat("::: {#refs}\n");
  cat(":::\n\n");
```

<!-- tables, if not child doc and lstTbls is not empty -->
```{r}
#| label: tables_SrvData
#| eval: !expr '!knitr::opts_knit$get("child")'
#| results: asis
  source(system.file("files/printTablesSectionFromList.R",package="wtsQMD"));
```

<!-- figures, if not child doc and lstFigs is not empty -->
```{r}
#| label: figures_SrvData
#| eval: !expr '!knitr::opts_knit$get("child")'
#| results: asis
  source(system.file("files/printFiguresSectionFromList.R",package="wtsQMD"));
```
