---
title: "Comparison of NMFS survey results from `crabpack` with the 2023 PIBKC assessment"
author: "William T. Stockhausen"
institute: NOAA/NMFS/AFSC
date: '`r format(Sys.time(), "%b %e, %Y")`'
fontsize: 11pt 
number-sections: true
reference-location: document
bibliography: '`r path.expand("~/Work/Projects/Bibliography/AllRefs.bib")`'
csl: '`r system.file("files/CJFAS.csl",package="wtsQMD")`'
link-citations: true
crossref:
  chapters: false      # prepend label reference numbers by chater number?
  fig-title: Figure    # for caption: default is "Figure")
  tbl-title: Table     # for caption: default is "Table")
  title-delim: "."     # for caption: default is ":")
  fig-prefix: Figure   # for in-text (use [-@fig-ref] to drop prefix in text)
  tbl-prefix: Table    # for in-text (use [-@tbl-ref] to drop prefix in text)
  fig-labels: arabic    # options are arabic, roman, roman i, alpha x, alpha X; latter two starting from x/X
  tbl-labels: arabic    # options are arabic, roman, roman i, alpha x, alpha X; latter two starting from x/X
  subref-labels: alpha a # options are arabic, roman, roman i, alpha x, alpha X; latter two starting from x/X
  ref-hyperlink: true    # references are hyperlinked if true
format: 
  html: 
    df-print: paged
    toc: true
    toc-location: right
    fig-width: 8
    fig-asp: 1.4
    fig-dpi: 100
    embed-resources: true
    include-in-header: 
      - '`r system.file("files/in-line_math_mode.html",package="wtsQMD")`'
  pdf:
    documentclass: scrartcl
    toc: false
    fig_crop: false
    keep-tex: false
    geometry:
      - left=1.0in
      - right=1.0in
      - top=1.0in
      - bottom=1.0in
      - textwidth=6.5in
      - showframe=false
    include-in-header: 
      - text: |
          \usepackage{placeins}
          \extrafloats{500}
          \maxdeadcycles=10000
          \usepackage{fontspec}
          \usepackage{multicol}
          \usepackage{hhline}
          \newlength\Oldarrayrulewidth
          \newlength\Oldtabcolsep
      - file: '`r system.file("files/ltx_ExtraLatexIncludes.tex",package="wtsQMD")`'
echo: false
warning: false
results: 'hide'
keep-md: false
keep-yaml: false
editor: source
editor_options: 
  chunk_output_type: console
concordance: true
params:
  setup: !expr 'system.file("files/qmd_setup.R",package="wtsQMD")'
  dirAsmt: "~/Work/StockAssessments-Crab/Assessments/TannerCrab/2023-09.PIBKC"
  testing: false
---
<!-- IMPORTANT: if used as a child doc, all chunk labels must be unique within the overall document -->

<!-- 
  NOTEs: 
     * child_path$peek() gives path to current script.
     * before starting a child document, do 
         "child_path$push(file.path(child_path$peek(),rel_path))" first, 
         where rel_path is the relative path to the child
     * after a child document has finished, do "child_path$pop()" to return to current path value
-->

<!-- if not child doc, set up required objects -->
```{r}
#| label: CrabPack_setup
#| eval: !expr '!knitr::opts_knit$get("child")'
#| results: "asis"
  testing = params$testing;
  if (testing) cat(params$setup,"\n\n")
  source(params$setup);
  if (testing) cat("root = ",root,"\n\n")
```

```{r}
#| label: setup_CrabPack
#| results: 'asis'
  require(crabpack);
  require(ggplot2);
  require(kableExtra);
  require(tables);
  
  #--path to folder containing "this" file
  dirThs = child_path$peek();

  #--constants
  MILLION  = 1000000;
  THOUSAND = 1000;

  #--survey years to include
  yrs = 1975:2024;
```

```{r CrabPack_getSurveyData}
  #--get my PIBKC crab survey results (run r_wts.PIBKC.doCalcs.R)----
  lstWTS = wtsUtilities::getObj(file.path(dirThs,"rda_wts.PIBKC.NMFS.RData"));
  
  #--PIBKC data from crabpack----
  if (FALSE){
    lstCP = get_specimen_data(species="BKC",
                              region="EBS",
                              district="PRIB",
                              channel="API");
    wtsUtilities::saveObj(lstCP,file.path(dirThs,"rda_crabpack_specimen_data.PIBKC.RData"));
  } else {
    lstCP = wtsUtilities::getObj(file.path(dirThs,"rda_crabpack_specimen_data.PIBKC.RData"));
  }
```

```{r CrabPack_calcSurveyABs}
  #--Biomass and abundance----
  ##--extract TCSAM02 biomass/abundance time series for PIBKC
  dfrW_ABs = lstWTS$dfrACD.ByX.PD |> 
                dplyr::select(y=YEAR,
                              STRATUM_AREA,
                              xm=SEX,
                              x=SEXp,
                              abd=totABUNDANCE,
                              abdCV=cvABUNDANCE,
                              bio=totBIOMASS,
                              bioCV=cvBIOMASS) |> 
                dplyr::mutate(type="asmt",
                              abd=MILLION*abd,
                              bio=THOUSAND*bio);
  #head(dfrW_ABs);
  ##--get crabpack biomass/abundance time series----
  dfrC_ABs = calc_bioabund(lstCP,
                          species="BKC",
                          region="EBS",
                          district="PRIB",
                          years=1975:2024,
                          sex="all_categories", #  c("male","female"),
                          crab_category="all_categories",
                          spatial_level="district") |> 
          dplyr::select(y=YEAR,
                        STRATUM_AREA=TOTAL_AREA,
                        xm=CATEGORY,
                        x=SEX_TEXT,
                        abd=ABUNDANCE,
                        abdCV=ABUNDANCE_CV,
                        bio=BIOMASS_MT,
                        bioCV=BIOMASS_MT_CV) |> 
          dplyr::mutate(type="crabpack",
                        xm=paste0(stringr::str_replace(xm,"_"," "),"s"));
  #head(dfrC_ABs);
  
  dfrABs = dplyr::bind_rows(dfrW_ABs,dfrC_ABs) |> 
             dplyr::filter(xm %in% unique(dfrC_ABs$xm));

  #--calculate differences in abundance
  dfrAsp = dfrABs |> dplyr::select(y,xm,abd,type) |> 
              tidyr::pivot_wider(names_from="type",values_from="abd") |> 
              dplyr::mutate(diff=asmt-crabpack,
                            pdif=2*100*diff/(asmt+crabpack));
  #--calculate differences in biomass
  dfrBsp = dfrABs |> dplyr::select(y,xm,bio,type) |> 
              tidyr::pivot_wider(names_from="type",values_from="bio") |> 
              dplyr::mutate(diff=asmt-crabpack,
                            pdif=2*100*diff/(asmt+crabpack));
```

## Crabpack comparisons

The ASFC's Shellfish Assessment Program has introduced `crabpack`, a new R package [@ref-R] to access NMFS EBS crab survey data and subsequently estimate annual abundance, biomass, and size compositions by year for several population categories (e.g., sex, maturity state). The [tcsamSurveyData](https://github.com/wStockhausen/tcsamSurveyData) R package has been used previously with survey haul data files downloaded from [AKFIN](https://akfin.psmfc.org) Answers to provide similar information for the PIBKC stock assessment [e.g., @PIBKC2023]. Here, the two approaches are compared for the Pribilof District abundance, biomass, and size compositions for NMFS EBS crab survey data for PIBKC from 1975 to 2023.

### Survey abundance estimates

Estimates of Pribilof District abundance from the NMFS bottom trawl survey for male and female PIBKC by population state are compared by year in [@fig-CrabPack-SrvAbd] for calculations made in the 2023 assessment [@PIBKC2023] and with the `crabpack` R package. Absolute differences and percent differences between the two methods are shown, respectively, in Figures [-@fig-CrabPack-SrvAbdAbsDif] and [-@fig-CrabPack-SrvAbdPctDif]. The percent differences are also shown in Table [-@tbl-CrabPack-SrvAbdPctDif] to two decimal places. The figures and table show excellent agreement between the two methods in all survey years except 1979, when estimates from the two methods differ substantially (> 10%). The estimates from the assessment are larger than those from `crabpack` in 1979. The differences in the two methods may reflect differences in the stratum areas used to expand mean CPUE (numbers/area) within a stratum to stratum abundance or in the actual hauls included in the calculation (`crabpack` appears to include hauls at corner stations that were only conducted in 1979, while these were excluded in the standardized time series used in the assessment).

```{r}
#| label: fig_CrabPack-SrvAbd
#| results: asis
#| fig-width: 9
#| fig-asp: 0.7
  p1 = ggplot(dfrABs |> dplyr::mutate(abd=abd/MILLION) |> dplyr::filter(y<1985),
              aes(x=y,y=abd,ymin=abd*(1-abdCV),ymax=abd*(1+abdCV),colour=type,fill=type,shape=type)) + 
       geom_ribbon(alpha=0.3) + geom_line() + geom_point(fill=NA,size=3) + 
       scale_y_log10(limits=c(0.01,NA),oob=scales::squish) + 
       scale_fill_manual(values=c("gold","blue"),aesthetics=c("colour","fill")) + 
       scale_x_continuous(breaks=seq(1970,3000,2)) +
       scale_shape_manual(values=c(24,25)) + 
       facet_grid(xm~.,scales="free_y") + 
       labs(y="Abundance (millions)") + 
       wtsPlots::getStdTheme() + 
       theme(axis.title.x=element_blank(),
             strip.text.y=element_blank(),
             legend.title=element_blank(),
             legend.position="none",
             legend.position.inside=c(0.99,0.99),
             legend.justification=c(1,1));
  p2 = ggplot(dfrABs |> dplyr::mutate(abd=abd/MILLION) |> dplyr::filter(y>=1985),
              aes(x=y,y=abd,ymin=abd*(1-abdCV),ymax=abd*(1+abdCV),colour=type,fill=type,shape=type)) + 
       geom_ribbon(alpha=0.3) + geom_line() + geom_point(fill=NA,size=3) + 
       scale_y_log10(limits=c(0.01,NA),oob=scales::squish) + 
       scale_fill_manual(values=c("gold","blue"),aesthetics=c("colour","fill")) + 
       scale_x_continuous(breaks=seq(1970,3000,5)) +
       scale_shape_manual(values=c(24,25)) + 
       facet_grid(xm~.,scales="free_y") + 
       labs(y="Abundance (millions)") + 
       wtsPlots::getStdTheme() + 
       theme(axis.title.x=element_blank(),
             axis.title.y=element_blank(),
             legend.title=element_blank(),
             legend.position="inside",
             legend.position.inside=c(0.99,0.99),
             legend.justification=c(1,1));
  pg = cowplot::plot_grid(p1,p2,nrow=1,rel_widths=c(1,2.5));
  cap = paste0("Comparison of annual estimates of design-based area-swept abundance ",
               "from the NMFS EBS bottom trawl survey by the 2023 PIBKC assessment (*asmt*) and ",
               "the `crabpack` R package (*crabpack*), by population category.");
  lbl = wtsQMD::getLabel();
  pth = wtsQMD::getFigFN();
  lstFigs = c(lstFigs,wtsQMD::printGGplot(pg,lbl=lbl,cap=cap,pth=pth,ori="L"));
```

```{r}
#| label: fig_CrabPack-SrvAbdAbsDif
#| results: asis
#| fig-width: 9
#| fig-asp: 0.7
  p1 = ggplot(dfrAsp |> dplyr::mutate(diff=diff/MILLION) |> dplyr::filter(y<1985),
              aes(x=y,y=diff)) + 
       geom_line() + geom_point(fill=NA,size=3) + 
       geom_hline(yintercept=0,linetype=3) + 
       scale_fill_manual(values=c("gold","blue"),aesthetics=c("colour","fill")) + 
       scale_x_continuous(breaks=seq(1970,3000,2)) +
       scale_shape_manual(values=c(24,25)) + 
       facet_grid(xm~.) + 
       labs(y="Abundance Difference (millions)") + 
       wtsPlots::getStdTheme() + 
       theme(axis.title.x=element_blank(),
             strip.text.y=element_blank(),
             legend.title=element_blank(),
             legend.position="none",
             legend.position.inside=c(0.99,0.99),
             legend.justification=c(1,1));
  p2 = ggplot(dfrAsp |> dplyr::mutate(diff=diff/MILLION) |> dplyr::filter(y>=1985),
              aes(x=y,y=diff)) + 
       geom_line() + geom_point(fill=NA,size=3) + 
       geom_hline(yintercept=0,linetype=3) + 
       scale_fill_manual(values=c("gold","blue"),aesthetics=c("colour","fill")) + 
       scale_x_continuous(breaks=seq(1970,3000,5)) +
       scale_shape_manual(values=c(24,25)) + 
       facet_grid(xm~.) + 
       labs(y="Abundance Difference (millions)") + 
       wtsPlots::getStdTheme() + 
       theme(axis.title.x=element_blank(),
             axis.title.y=element_blank(),
             legend.title=element_blank(),
             legend.position="inside",
             legend.position.inside=c(0.99,0.99),
             legend.justification=c(1,1));
  pg = cowplot::plot_grid(p1,p2,nrow=1,rel_widths=c(1,2.5));
  cap = paste0("Differences in annual estimates of design-based area-swept abundance ",
               "from the NMFS EBS bottom trawl survey by the 2023 PIBKC assessment and ",
               "the `crabpack` R package, by population category.");
  lbl = wtsQMD::getLabel();
  pth = wtsQMD::getFigFN();
  lstFigs = c(lstFigs,wtsQMD::printGGplot(pg,lbl=lbl,cap=cap,pth=pth,ori="L"));
```

```{r}
#| label: fig_CrabPack-SrvAbdPctDif
#| results: asis
#| fig-width: 9
#| fig-asp: 0.7
  p1 = ggplot(dfrAsp |> dplyr::filter(y<1985), aes(x=y,y=pdif)) + 
       geom_line() + geom_point(fill=NA,size=3) + 
       geom_hline(yintercept=0,linetype=3) + 
       scale_fill_manual(values=c("gold","blue"),aesthetics=c("colour","fill")) + 
       scale_x_continuous(breaks=seq(1970,3000,2)) +
       scale_shape_manual(values=c(24,25)) + 
       facet_grid(xm~.) + 
       labs(y="% Difference in Abundance") + 
       wtsPlots::getStdTheme() + 
       theme(axis.title.x=element_blank(),
             strip.text.y=element_blank(),
             legend.title=element_blank(),
             legend.position="none",
             legend.position.inside=c(0.99,0.99),
             legend.justification=c(1,1));
  p2 = ggplot(dfrAsp |> dplyr::filter(y>=1985), aes(x=y,y=pdif)) + 
       geom_line() + geom_point(fill=NA,size=3) + 
       geom_hline(yintercept=0,linetype=3) + 
       scale_fill_manual(values=c("gold","blue"),aesthetics=c("colour","fill")) + 
       scale_x_continuous(breaks=seq(1970,3000,5)) +
       scale_shape_manual(values=c(24,25)) + 
       facet_grid(xm~.) + 
       labs(y="% Difference in Abundance") + 
       wtsPlots::getStdTheme() + 
       theme(axis.title.x=element_blank(),
             axis.title.y=element_blank(),
             legend.title=element_blank(),
             legend.position="inside",
             legend.position.inside=c(0.99,0.99),
             legend.justification=c(1,1));
  pg = cowplot::plot_grid(p1,p2,nrow=1,rel_widths=c(1,2.5));
  cap = paste0("Percent differences in annual estimates of design-based area-swept abundance ",
               "from the NMFS EBS bottom trawl survey by the 2023 PIBKC assessment and ",
               "the `crabpack` R package, by population category.");
  lbl = wtsQMD::getLabel();
  pth = wtsQMD::getFigFN();
  lstFigs = c(lstFigs,wtsQMD::printGGplot(pg,lbl=lbl,cap=cap,pth=pth,ori="L"));
```

```{r tbl.CrabPack-SrvAbdPctDif}
#| results: asis
  tblr = tabular(Factor(y,name="year") ~ Factor(xm)*pdif*mean,
                 data=dfrAsp |> dplyr::mutate(pdif=round(pdif,1)));
  colLabels(tblr) = colLabels(tblr)[2,];
  kblr = tblr |> wtsQMD::convert_tblr_to_kbl(col_spec=c(1),!isPDF,
                                             ltx_font_size=7,replaceNAs="--",adjColSpacing=-4);
  cap = paste0("Percent difference, by year, in  design-based NMFS survey abundance trends ",
               "from the 2023 PIBKC assessment and the `crabpack` R package, by population category. ",
               "NaN: indicates that no crab in the category were caught.");
  lstTbls = c(lstTbls,
              wtsQMD::insertKblIntoQMD(kblr,
                                       lbl="tbl-CrabPack-SrvAbdPctDif", 
                                       cap=cap,
                                       ori="P"));
  rm(tblr,kblr,cap);
```

### Survey biomass estimates

Estimates of EBS-wide biomass from the NMFS bottom trawl survey for male and female PIBKC by maturity state are compared by year in [@fig-CrabPack-SrvBio] for calculations made in the 2023 assessment [@PIBKC2023] and with the `crabpack` R package. Absolute differences and percent differences between the two methods are shown, respectively, in Figures [-@fig-CrabPack-SrvBioAbsDif] and [-@fig-CrabPack-SrvBioPctDif]. The percent differences are also shown in Table [-@tbl-CrabPack-SrvBioPctDif] to two decimal places. 

As with abundance, the figures and table demonstrate excellent agreement between the two methods in all survey years prior to 2016 except 1979, when estimates from the two methods differ substantially (> 10%). Unlike the abundance estimates, the two methods also exhibit small differences (< 5 %) in 2016 and subsequent years. The estimates from the assessment for 2016 and later are larger than those from `crabpack` in all years. The post-2015 differences between the two methods may reflect differences in the size used to calculate the weight of individual crab: the assessment uses carapace width to the first decimal place while `crabpack` apparently uses the carapace width to 1-mm.

```{r}
#| label: fig_CrabPack-SrvBio
#| results: asis
#| fig-width: 9
#| fig-asp: 0.7
  p1 = ggplot(dfrABs |> dplyr::mutate(bio=bio/THOUSAND) |> dplyr::filter(y<1985),
              aes(x=y,y=bio,ymin=bio*(1-bioCV),ymax=bio*(1+bioCV),colour=type,fill=type,shape=type)) + 
       geom_ribbon(alpha=0.3,colour=NA) + geom_line() + geom_point(fill=NA,size=3) + 
       scale_fill_manual(values=c("gold","blue"),aesthetics=c("colour","fill")) + 
       scale_x_continuous(breaks=seq(1970,3000,2)) +
       scale_shape_manual(values=c(24,25)) + 
       facet_grid(xm~.,scales="free") + 
       labs(y="Biomass (1000's t)") + 
       wtsPlots::getStdTheme() + 
       theme(axis.title.x=element_blank(),
             legend.title=element_blank(),
             strip.text.y=element_blank(),
             legend.position="none",
             legend.position.inside=c(0.99,0.99),
             legend.justification=c(1,1));
  p2 = ggplot(dfrABs |> dplyr::mutate(bio=bio/THOUSAND) |> dplyr::filter(y>=1985),
              aes(x=y,y=bio,ymin=bio*(1-bioCV),ymax=bio*(1+bioCV),colour=type,fill=type,shape=type)) + 
       geom_ribbon(alpha=0.3,colour=NA) + geom_line() + geom_point(fill=NA,size=3) + 
       scale_fill_manual(values=c("gold","blue"),aesthetics=c("colour","fill")) + 
       scale_x_continuous(breaks=seq(1970,3000,5)) +
       scale_shape_manual(values=c(24,25)) + 
       facet_grid(xm~.,scales="free") + 
       labs(y="Biomass (1000's t)") + 
       wtsPlots::getStdTheme() + 
       theme(axis.title.x=element_blank(),
             axis.title.y=element_blank(),
             legend.title=element_blank(),
             legend.position="inside",
             legend.position.inside=c(0.99,0.99),
             legend.justification=c(1,1));
  pg = cowplot::plot_grid(p1,p2,nrow=1,rel_widths=c(1,2.5));
  cap = paste0("Comparison of annual estimates of design-based area-swept biomass ",
               "from the NMFS EBS bottom trawl survey by the 2023 PIBKC assessment (*asmt*) and ",
               "the `crabpack` R package (*crabpack*), by population category.");
  lbl = wtsQMD::getLabel();
  pth = wtsQMD::getFigFN();
  lstFigs = c(lstFigs,wtsQMD::printGGplot(pg,lbl=lbl,cap=cap,pth=pth,ori="L"));
```

```{r}
#| label: fig_CrabPack-SrvBioAbsDif
#| results: asis
#| fig-width: 9
#| fig-asp: 0.7
  p1 = ggplot(dfrBsp |> dplyr::mutate(diff=diff/THOUSAND) |> dplyr::filter(y<1985),
              aes(x=y,y=diff)) + 
       geom_line() + geom_point(fill=NA,size=3) + 
       geom_hline(yintercept=0,linetype=3) + 
       scale_fill_manual(values=c("gold","blue"),aesthetics=c("colour","fill")) + 
       scale_x_continuous(breaks=seq(1970,3000,2)) +
       scale_shape_manual(values=c(24,25)) + 
       facet_grid(xm~.) + 
       labs(y="Biomass Difference (1,000's t)") + 
       wtsPlots::getStdTheme() + 
       theme(axis.title.x=element_blank(),
             strip.text.y=element_blank(),
             legend.title=element_blank(),
             legend.position="none",
             legend.position.inside=c(0.99,0.99),
             legend.justification=c(1,1));
  p2 = ggplot(dfrBsp |> dplyr::mutate(diff=diff/THOUSAND) |> dplyr::filter(y>=1985),
              aes(x=y,y=diff)) + 
       geom_line() + geom_point(fill=NA,size=3) + 
       geom_hline(yintercept=0,linetype=3) + 
       scale_fill_manual(values=c("gold","blue"),aesthetics=c("colour","fill")) + 
       scale_x_continuous(breaks=seq(1970,3000,5)) +
       scale_shape_manual(values=c(24,25)) + 
       facet_grid(xm~.) + 
       labs(y="Biomass Difference (1,000's t)") + 
       wtsPlots::getStdTheme() + 
       theme(axis.title.x=element_blank(),
             axis.title.y=element_blank(),
             legend.title=element_blank(),
             legend.position="inside",
             legend.position.inside=c(0.99,0.99),
             legend.justification=c(1,1));
  pg = cowplot::plot_grid(p1,p2,nrow=1,rel_widths=c(1,2.5));
  cap = paste0("Differences in annual estimates of design-based area-swept biomass ",
               "from the NMFS EBS bottom trawl survey by the 2023 PIBKC assessment and ",
               "the `crabpack` R package, by population category.");
  lbl = wtsQMD::getLabel();
  pth = wtsQMD::getFigFN();
  lstFigs = c(lstFigs,wtsQMD::printGGplot(pg,lbl=lbl,cap=cap,pth=pth,ori="L"));
```

```{r}
#| label: fig_CrabPack-SrvBioPctDif
#| results: asis
#| fig-width: 9
#| fig-asp: 0.7
  p1 = ggplot(dfrBsp |> dplyr::filter(y<1985), aes(x=y,y=pdif)) + 
       geom_line() + geom_point(fill=NA,size=3) + 
       geom_hline(yintercept=0,linetype=3) + 
       scale_fill_manual(values=c("gold","blue"),aesthetics=c("colour","fill")) + 
       scale_x_continuous(breaks=seq(1970,3000,2)) +
       scale_shape_manual(values=c(24,25)) + 
       facet_grid(xm~.) + 
       labs(y="% Difference in Biomass") + 
       wtsPlots::getStdTheme() + 
       theme(axis.title.x=element_blank(),
             strip.text.y=element_blank(),
             legend.title=element_blank(),
             legend.position="none",
             legend.position.inside=c(0.99,0.99),
             legend.justification=c(1,1));
  p2 = ggplot(dfrBsp |> dplyr::filter(y>=1985), aes(x=y,y=pdif)) + 
       geom_line() + geom_point(fill=NA,size=3) + 
       geom_hline(yintercept=0,linetype=3) + 
       scale_fill_manual(values=c("gold","blue"),aesthetics=c("colour","fill")) + 
         scale_x_continuous(breaks=seq(1970,3000,5)) +
       scale_shape_manual(values=c(24,25)) + 
       facet_grid(xm~.) + 
       labs(y="% Difference in Biomass") + 
       wtsPlots::getStdTheme() + 
       theme(axis.title.x=element_blank(),
             axis.title.y=element_blank(),
             legend.title=element_blank(),
             legend.position="inside",
             legend.position.inside=c(0.99,0.99),
             legend.justification=c(1,1));
  pg = cowplot::plot_grid(p1,p2,nrow=1,rel_widths=c(1,2.5));
  cap = paste0("Percent differences in annual estimates of design-based area-swept biomass ",
               "from the NMFS EBS bottom trawl survey by the 2023 PIBKC assessment and ",
               "the `crabpack` R package, by population category.");
  lbl = wtsQMD::getLabel();
  pth = wtsQMD::getFigFN();
  lstFigs = c(lstFigs,wtsQMD::printGGplot(pg,lbl=lbl,cap=cap,pth=pth,ori="L"));
```

```{r tbl.CrabPack-SrvBioPctDif}
#| results: asis
  tblr = tabular(Factor(y,name="year") ~ Factor(xm)*pdif*mean,
                 data=dfrBsp |> dplyr::mutate(pdif=round(pdif,1)));
  colLabels(tblr) = colLabels(tblr)[2,];
  kbl = tblr |> wtsQMD::convert_tblr_to_kbl(col_spec=c(1),isHTM,
                                            ltx_font_size=7,replaceNAs="--",adjColSpacing=-4);
  cap = paste0("Percent difference, by year, in design-based NMFS survey biomass trends ",
               "from the 2023 PIBKC assessment and the `crabpack` R package, by population category. ",
               "NaN: indicates that no crab in the category were caught.");
  lstTbls = c(lstTbls,
              wtsQMD::insertKblIntoQMD(kbl,
                                       lbl="tbl-CrabPack-SrvBioPctDif", 
                                       cap=cap,
                                       ori="P"));
  rm(tblr,kbl,cap);
```

<!-- references, if not child doc -->
```{r,eval=!knitr::opts_knit$get("child"),results='asis'}
  cat("# References {-}\n");
  cat("::: {#refs}\n");
  cat(":::\n\n");
```

<!-- tables, if not child doc and lstTbls is not empty -->
```{r}
#| label: tables_CrabPack
#| eval: !expr '!knitr::opts_knit$get("child")'
#| results: asis
  source(system.file("files/printTablesSectionFromList.R",package="wtsQMD"));
```

<!-- figures, if not child doc and lstFigs is not empty -->
```{r}
#| label: figures_CrabPack
#| eval: !expr '!knitr::opts_knit$get("child")'
#| results: asis
  source(system.file("files/printFiguresSectionFromList.R",package="wtsQMD"));
```
