---
title: "2025 PIBKC Assessment Considerations"
author:
- name: William T. Stockhausen
  affiliations:
    - id: afsc-refm
      name: "Alaska Fisheries Science Center"
      department: "Resource Ecology and Fisheries Management"
      address: 
        - "7600 Sand Point Way N.E."
        - "Seattle, Washington 98115-6349"
date: '`r format(Sys.time(), "%b %e, %Y")`'
fontsize: 11pt 
number-sections: true
number-depth: 3
reference-location: document
reference-section-title: References
bibliography: '`r path.expand("~/Work/Projects/Bibliography/AllRefs.bib")`'
csl: '`r system.file("files/CJFAS.csl",package="wtsQMD")`'
link-citations: true
crossref:
  chapters: false      # prepend label reference numbers by chater number?
  fig-title: Figure    # for caption: default is "Figure")
  tbl-title: Table     # for caption: default is "Table")
  title-delim: "."     # for caption: default is ":")
  fig-prefix: Figure   # for in-text (use [-@fig-ref] to drop prefix in text)
  tbl-prefix: Table    # for in-text (use [-@tbl-ref] to drop prefix in text)
  fig-labels: arabic    # options are arabic, roman, roman i, alpha x, alpha X; latter two starting from x/X
  tbl-labels: arabic    # options are arabic, roman, roman i, alpha x, alpha X; latter two starting from x/X
  subref-labels: alpha a # options are arabic, roman, roman i, alpha x, alpha X; latter two starting from x/X
  ref-hyperlink: true    # references are hyperlinked if true
format: 
  html: 
    df-print: paged
    toc: true
    toc-location: right
    fig-width: 8
    fig-asp: 0.4
    fig-dpi: 100
    embed-resources: true
    include-in-header: 
      - '`r system.file("files/in-line_math_mode.html",package="wtsQMD")`'
  pdf:
    documentclass: scrartcl
    toc: false
    fig_crop: false
    keep-tex: false
    fig-width: 6.5
    fig-asp: 0.4
    geometry:
      - left=1.0in
      - right=1.0in
      - top=1.0in
      - bottom=1.0in
      - textwidth=6.5in
      - showframe=false
    include-in-header: 
      - text: |
          \usepackage{placeins}
          \extrafloats{500}
          \maxdeadcycles=10000
          \usepackage{fontspec}
          \usepackage{multicol}
          \usepackage{hhline}
          \newlength\Oldarrayrulewidth
          \newlength\Oldtabcolsep
      - file: '`r system.file("files/ltx_ExtraLatexIncludes.tex",package="wtsQMD")`'
echo: false
message: false
warning: false
results: 'hide'
keep-md: true
keep-yaml: false
editor: source
editor_options: 
  chunk_output_type: console
concordance: true
params:
  setup: !expr 'system.file("files/qmd_setup.R",package="wtsQMD")'
  rdaAsmtSetup: "rda_AssessmentSetup.RData"
  testing: false
  reorderTables: false   #--issue with finding "range" of table values  (don't use)
  reorderFigures: false  #--issue with finding "range" of figure values (don't use)
---
<!-- IMPORTANT: if used as a child doc, all chunk labels must be unique within the overall document -->

<!-- 
  NOTEs: 
     * child_path$peek() gives path to current script folder.
     * before starting a child document, do 
         "child_path$push(file.path(child_path$peek(),rel_path))" first, 
         where rel_path is the relative path to the child
     * after a child document has finished, do "child_path$pop()" to return to current path value
-->

<!-- if not child doc, set up required objects -->
```{r}
#| label: REPT_setup
#| eval: !expr '!knitr::opts_knit$get("child")'
#| results: "asis"
  testing = params$testing;
  if (testing) cat(params$setup,"\n\n")
  source(params$setup);
  if (testing) cat("root = ",root,"\n\n")
  reorderTables  = params$reorderTables;
  reorderFigures = params$reorderFigures;
```

```{r}
#| label: setup_REPT
#| results: 'asis'
  require(ggplot2);
  require(kableExtra);
  require(tables);
  Sum = wtsUtilities::Sum;
  old_thm = ggplot2::theme_set(cowplot::theme_cowplot(font_size = 10) +
                               cowplot::background_grid() +
                               cowplot::panel_border());
  thm = wtsPlots::getStdTheme();
  options("readr.show_col_types"=FALSE);
  if (testing) cat("dirThs =",child_path$peek(),"\n\n")
  ##--NOTE: take out or modify the following as necessary
  if (!exists("s")){
    if (rstudioapi::isAvailable())
      fn = file.path(rstudioapi::getActiveProject(),"rda_ProjectSetup.RData");
    if (child_path$peek()!="")
      fn = file.path(child_path$peek(),"../rda_ProjectSetup.RData");
    #--for debugging: ;
    if (file.exists(fn)) s = wtsUtilities::getObj(fn);
  }
  ##--
```

\begin{center}
THIS INFORMATION IS DISTRIBUTED SOLELY FOR THE PURPOSE OF 
PREDISSEMINATION PEER REVIEW UNDER APPLICABLE INFORMATION QUALITY GUIDELINES. 
IT HAS NOT BEEN FORMALLY DISSEMINATED BY NOAA FISHERIES/ALASKA FISHERIES SCIENCE CENTER AND 
SHOULD NOT BE CONSTRUED TO REPRESENT ANY AGENCY DETERMINATION OR POLICY
\end{center}


# Introduction 

The next full assessment for the Pribilof Islands blue king crab (PIBKC) stock will be reviewed by the Crab Plan Team (CPT) in September 2025 and the NPFMC's Science and Statistical Committee (SSC) in October 2025. The stock has been on a two-year cycle for assessment and the last full assessment was conducted in September 2023 [@PIBKC2023]. Following the September 2025 assessment, the stock will begin a four-year assessment cycle and the next full assessment will be conducted in 2029. 

This report primarily addresses a number of issues related to data from the NMFS EBS bottom trawl survey for PIBKC that have arisen since the last assessment. First, AFSC's Shellfish Assessment Program (SAP) has developed an R package, "crabpack", as a replacement to AKFIN Answers (https://akfin.psmfc.org) for obtaining crab-related survey data in a standard format. SAP requested that assessment authors test the package and compare results of data pulls using the package with data pulled using the authors' previous methods. Second, as part of the effort to "modernize" the NMFS EBS bottom trawl survey to improve efficiency, the high-density "corner" stations in the NMFS EBS survey grid near the Pribilof Islands and St. Matthew Island were dropped for the 2024 survey and will not be sampled in future surveys. Assessment authors were asked to consider the impact of this change on their assessment. Finally, the 2023 and 2024 surveys found no mature male blue king crab in the Pribilof Islands sampling strata. While this is principally a consequence of applying relatively low sampling effort to a stock at low (but non-zero) abundance, the "hard zeros" introduced in the time series of mature male biomass for PIBKC can be problematic for the subsequent assessment. Several approaches to dealing with this issue are considered here. 

This report is organized into the following sections: Responses to previus CPT and SSC Comments (@sec-Resps), "New" Data and Analyses (@sec-NDAs), Summary (@sec-Smry), and Acknowledgments (@sec-Acks).

<!-- # Responses to CPT and SSC Comments {#sec-Resps} -->
```{r sct_Resps, child=file.path(child_path$peek(),"q01_PIBKC_ResponsesToComments2025.qmd")}
```

<!-- # "New" Data and Analyses {#sec-NDAs} -->
```{r sct_NDAs, child=file.path(child_path$peek(),"q02_NewDataAndAnalyses.qmd")}
```

# Summary {#sec-Smry}

The author looks forward to accessing the NMFS EBS bottom trawl survey data for crab using `crabpack` for the 2025 assessments. However, the author recommends  

  * using the full-precision carapace length measurements with the current length-weight regressions to calculate biomass from NMFS EBS survey abundance and size data
  * dropping the "extra" corner stations not included in the standard 375 stations from the 1979 NMFS EBS survey

With regard to inclusion of historical data from the (now discontinued) corner stations in time series for future assessments, the author recommends that they continue to be included in estimates of abundance/biomass and size compositions. It would be worthwhile to consider whether using a spatially-explicit, model-based approach like `sdmTMB` to derive indices of abundance/biomass that takes into account changes in spatial relationships in both the data and the sampling regimes to minimize potential biases across the time series and better capture changes in uncertainty.

With regard to "filling in the zeros" in the PIBKC design-based time series for MMB, the author looks forward to discussions with the CPT and SSC regarding the potential tradeoffs between the relative simplicity of the `rema` approaches and more statistically-defensible approaches like spatially-explicit model-based approach like `sdmTMB`. The author's recommendation is that `sdmTMB` be adopted as the modeling platform in the 2025 stock assessment to provide this index

# Acknowledgments {#sec-Acks}

The author would like to acknowledge and thank Shannon Hennessey (AFSC-SAP) for developing `crabpack`, Cole Monnahan (AFSC-SSMA) and Jane Sullivan (AFSC-MESA) for comments on the sampling-based approach to filling in time series zeros, Cole for help with interpreting `sdmTMB` results, and Lee Cronin-Fine (AFSC-SSMA) for providing an internal review of this document.


<!-- references -->
```{r,eval=!knitr::opts_knit$get("child"),results='asis'}
  cat("# References {-}\n");
  cat("::: {#refs}\n");
  cat(":::\n\n");
```

<!-- tables, if not child doc and lstTbls is not empty -->
```{r}
#| label: tables_REPT
#| eval: !expr '!knitr::opts_knit$get("child")'
#| results: asis
  source(system.file("files/printTablesSectionFromList.R",package="wtsQMD"));
```

<!-- figures, if not child doc and lstFigs is not empty -->
```{r}
#| label: figures_REPT
#| eval: !expr '!knitr::opts_knit$get("child")'
#| results: asis
  source(system.file("files/printFiguresSectionFromList.R",package="wtsQMD"));
```
